---
title: "Body Weight and Length - F0"
author: "Hamza"
date: "1 June 2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer, effects, interactions)
```

```{r}

# Load custom functions
source("../Scripts/functions_learning.R")
source("../Scripts/functions_repeatability.R")


```

#Import and filter data; also load models
```{r, include = FALSE}
#Master file with raw data
Data <- read.csv("../Data/Weight_Length/Analysis.csv")

#Filtered to ensure no spare tanks or fish are included in the analysis
Data_subset = filter(Data, Tank %in% c("HA_C1","HA_C2","HA_C3", "HA_C4", "HA_T1","HA_T2","HA_T3","HA_T4"))
Weight_Length_Data = filter(Data_subset, !Fish_ID %in% c("a6834","a6923","a7226","a7070","a7250","a7336","a7600","a7573","a7660","a6929","a6990","a7407","a7090","a7286","a7539","a6884","a7206","a7488","a6846","a7560","a7495","a7649","a7604","a7015","a7253","a7610","a7566","a7719","a7682","a7266","a7494","a7548","a7207"))

#Check structure
Weight_Length_Data$Sex <- as.factor(Weight_Length_Data$Sex)
Weight_Length_Data$Group <- as.factor(Weight_Length_Data$Group)
Weight_Length_Data$Week <- as.numeric(Weight_Length_Data$Week)
Weight_Length_Data$Fish_ID <- as.factor(Weight_Length_Data$Fish_ID)

#Subsetted data for later comparison of week 0 and final week
Week_0 <- subset(Weight_Length_Data, Weight_Length_Data$Week == "0")
Week_22 <- subset(Weight_Length_Data, Weight_Length_Data$Week == "22")

#Subseting data by control and treatment
Weight_Length_Control <- subset(Weight_Length_Data, Weight_Length_Data$Group == "Control") 
Weight_Length_Treatment <- subset(Weight_Length_Data, Weight_Length_Data$Group == "Treatment") 

#Load models
load("../Models/rpt_body_weight_control2.Rdata")
load("../Models/rpt_body_weight_treatment2.Rdata")


#Basic summary

Weight_Length_Data %>%                             
  dplyr::group_by(Group, Sex) %>%
  dplyr::summarise(count = n_distinct(Fish_ID))


```

### REPEATABILITY ANALYSIS FOR BODY WEIGHT AND LENGTH 
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION (FOR BOTH CONTROL AND TREATMENT)
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITIES
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT GROUPS

# Body Weight
```{r, echo=FALSE}




#Calculating repeatabilities (without week and with week)
# rpt_weight(Weight_Length_Control) -> rpt_body_weight_control #without week factored in
# 
# rpt_weight(Weight_Length_Treatment) -> rpt_body_weight_treatment #without week factored in

# rpt_weight2(Weight_Length_Control) -> rpt_body_weight_control2 #adjusted for week
# save(rpt_body_weight_control2, file = "../Models/rpt_body_weight_control2.Rdata")
# 
# rpt_weight2(Weight_Length_Treatment) -> rpt_body_weight_treatment2 #adjusted for week
# save(rpt_body_weight_treatment2, file = "../Models/rpt_body_weight_treatment2.Rdata")


#Obtaining within-individual and between-individual variance for body weight
# 
# rpt_within_weight(Weight_Length_Control) -> within_between_body_weight_control
# rpt_within_weight(Weight_Length_Treatment) -> within_between_body_weight_treatment
# 
# rpt_within_weight2(Weight_Length_Control) -> within_between_body_weight_control2 #adjusted for week
# save(within_between_body_weight_control2, file = "../Models/within_between_body_weight_control2.Rdata")
# rpt_within_weight2(Weight_Length_Treatment) -> within_between_body_weight_treatment2 #adjusted for week
# save(within_between_body_weight_treatment2, file = "../Models/within_between_body_weight_treatment2.Rdata")


#Obtaining differences between repeatabilities using custom made functions
Control_weight_boot <- unlist_rptr(rpt_body_weight_control2) 
Treatment_weight_boot <- unlist_rptr(rpt_body_weight_treatment2) 
body_weight_diff <- difference_boot(Control_weight_boot,Treatment_weight_boot) #calculating the difference
q_body_weight <- quantiles_diff_boot(body_weight_diff) #obtaining 95% CI
m_mody_weight <- mean(body_weight_diff) #Obtaining mean

q_body_weight
m_mody_weight

# Calculating difference in variance between control and treatment group 
#Weight_Length_Data$Group <- relevel(Weight_Length_Data$Group, ref="Treatment")


Model_Weight_1 <- lme(Weight.g. ~ Group*Sex + scale(Week, scale = FALSE), random = ~ 1| Fish_ID, data = Weight_Length_Data) #Mixed model without variance structure
summary(Model_Weight_1)
tab_model(Model_Weight_1)
contrasts_weight <- emmeans(Model_Weight_1, c("Group", "Sex"))
pairs(contrasts_weight)

e <- allEffects(Model_Weight_1)
print(e)
plot(e)


Model_Weight_2 <- lme(Weight.g. ~  Group*Sex + scale(Week, scale = FALSE), random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Weight_Length_Data) #mixed model with variance structure varIdent
summary(Model_Weight_2)
anova(Model_Weight_1, Model_Weight_2) #calculating difference between two models to find difference in variance
```

<!-- # Body Length (Not using body length data) -->
<!-- ```{r, echo=FALSE} -->

<!-- #Check Normality with mixed model and then histogram of residuals -->

<!-- Model_Body_Length <- lmer(Fish_Length_cm ~ Group + Sex + Week + (1 | Fish_ID), data = Weight_Length_Data) #mixed model  -->
<!-- tab_model(Model_Body_Length) -->
<!-- hist(residuals(Model_Body_Length))#histogram of residuals to check for normal distribution  -->

<!-- Model_Body_Length2 <- lmer(Fish_Length_cm ~ Group + Sex + Week + (1 | Fish_ID) + (1 + Week|Tank), data = Weight_Length_Data)  -->
<!-- summary(Model_Body_Length2) -->
<!-- tab_model(Model_Body_Length2) -->
<!-- hist(residuals(Model_Body_Length2)) -->



<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_length2(Weight_Length_Control) -> rpt_length_control -->
<!-- rpt_length_control -->
<!-- rpt_length2(Weight_Length_Treatment) -> rpt_length_treatment -->
<!-- rpt_length_treatment -->

<!-- #Obtaining within-individual and between-individual variance for body weight -->

<!-- rpt_within_length(Weight_Length_Control) -> within_between_body_length_control -->
<!-- rpt_within_length(Weight_Length_Treatment) -> within_between_body_length_treatment -->

<!-- #Obtaining differences between repeatabilities using custom made functions -->
<!-- Control_length_boot <- unlist_rptr(rpt_body_weight_control)  -->
<!-- Treatment_length_boot <- unlist_rptr(rpt_body_weight_treatment)  -->
<!-- body_length_diff <- difference_boot(Control_length_boot,Treatment_length_boot) #calculating the difference -->
<!-- q_body_length <- quantiles_diff_boot(body_length_diff) #obtaining 95% CI -->
<!-- m_mody_length <- mean(body_length_diff) #Obtaining mean -->

<!-- q_body_length -->
<!-- m_mody_length -->

<!-- # Calculating difference in variance between control and treatment group  -->
<!-- Model_Length_1 <- lme(Fish_Length_cm ~ Group*Week + Sex*Week, random = ~ 1| Fish_ID, data = Weight_Length_Data) #Mixed model without variance structure -->
<!-- summary(Model_Length_1) -->
<!-- Model_Length_2 <- lme(Fish_Length_cm ~ Group*Week + Sex*Week, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Weight_Length_Data) #mixed model with variance structure varIdent -->
<!-- summary(Model_Length_2) -->
<!-- anova(Model_Length_1, Model_Length_2) #calculating difference between two models to find difference in variance -->
<!-- ``` -->


# Visualizations
Boxplot to show distribution at beginning of the experiment and at the end of the experiment
```{r, echo = FALSE}
boxplot_0 <- ggplot(data = Week_0) +
  geom_boxplot(mapping = aes(x = Group, y = Weight.g., fill = Group)) +
  facet_grid(~Sex)
  
boxplot_0

boxplot_22 <- ggplot(data = Week_22) +
  geom_boxplot(mapping = aes(x = Group, y = Weight.g., fill = Group)) +
  facet_grid(~Sex)
  
boxplot_22

```  

<!-- # Mixed Models to account for week 0 -->
<!-- ```{r, echo = FALSE} -->
<!-- Weight_Model <- lmer(Weight.g. ~ Group + Week + Sex + (1|Fish_ID), data=Data) -->
<!-- tab_model(Weight_Model) -->

<!-- Weight_Model <- lmer(Weight.g. ~ Group*Week + Sex + (1|Fish_ID), data=Data) -->
<!-- tab_model(Weight_Model) -->

<!-- Weight_Model <- lmer(Weight.g. ~ Group*Week + Sex*Week  + (1|Fish_ID) + (1 + Week|Tank), data=Data) -->
<!-- tab_model(Weight_Model) -->

<!-- #A significant interaction exists between treatment and week as well as sex and week. What this means is that the treatment and control tanks have a different slope and this is also dependent on the week. This is also the case for the sexes, with the females having a steeper slope, also significantly different by the week.  -->


<!-- Weight_Model <- lmer(Fish_Length_cm ~ Group*Week + Sex*Week  + (1|Fish_ID) + (1 + Week|Tank), data=Data) -->
<!-- tab_model(Weight_Model) -->

<!-- model_week0_weight <- lmer(Weight.g. ~ Group + Sex + Fish_Length_cm + (1|Tank), data = Week_0 ) -->
<!-- tab_model(model_week0_weight) -->

<!-- model_week0_length <- lmer(Fish_Length_cm ~ Group + Sex + (1|Tank), data = Week_0 ) -->
<!-- tab_model(model_week0_length) -->


<!-- model_week0_bmi <- lmer(scale(BMI) ~ Group + Sex + (1|Tank), data = Week_0 ) -->
<!-- tab_model(model_week0_bmi) -->

<!-- lm_week0 <- glm(scale(BMI) ~ Group + Sex , data = Week_0 ) -->
<!-- tab_model(lm_week0) -->


<!-- lm_week0 <- glm(Weight.g. ~ Group + Sex , data = Week_0 ) -->
<!-- tab_model(lm_week0) -->

<!-- lm_week0 <- glm(Fish_Length_cm ~ Group + Sex , data = Week_0 ) -->
<!-- tab_model(lm_week0) -->

<!-- ``` -->


# plots (body weight)

```{r, echo = FALSE}
Summary_Weight <- summarySE(Weight_Length_Data, measurevar="Weight.g.", groupvars=c("Week","Group", "Sex"))

# So error bars aren't overlapping, we can use this:
pd <- position_dodge(0.1) # move them .05 to the left and right


line_plot_weight <- ggplot(Summary_Weight, aes(x=Week, y=Weight.g., colour=Group)) + 
    geom_errorbar(aes(ymin=Weight.g.-se, ymax=Weight.g.+se), colour="black", width=.3, position=pd) +
      scale_colour_manual(values = wes_palette("FantasticFox1", n = 2))+
    geom_line(position=pd) +
    geom_point(position=pd, size=3) +
  labs(title = "Obesogenic vs. Control Diet",
              subtitle = "Weight change after 22 weeks") +
  facet_grid(~Sex)

line_plot_weight

body_weight_violin <-  
  ggplot(data = Week_22,aes(x = Group, y = Weight.g., fill = Group))+
    scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+ 
    geom_violin(alpha=0.4, position = position_dodge(width = .75),size=1,color="black")+
    geom_boxplot(notch = TRUE,  outlier.size = -1, color="black",lwd=1.2, alpha = 0.7)+ 
    geom_point( shape = 21,size=2, position = position_jitterdodge(), color="black",alpha=1)+ 
    theme_pubr()+
    rremove("legend.title")+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"),legend.position = c(0.92, 0.85))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +font("legend.text",size = 15)+
    theme(legend.position = "none")+
  labs(title = "Final week of body weight measurements")+
    theme(axis.title.x=element_blank())+
   stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="red", fill="red") +
  facet_grid(~Sex)

body_weight_violin


body_weight_violin_overall <-  
  ggplot(data = Weight_Length_Data,aes(x = Group, y = Weight.g., fill = Group))+
    scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+ 
    geom_violin(alpha=0.4, position = position_dodge(width = .75),size=1,color="black")+
    geom_boxplot(notch = TRUE,  outlier.size = -1, color="black",lwd=1.2, alpha = 0.7)+ 
    geom_point( shape = 21,size=2, position = position_jitterdodge(), color="black",alpha=1)+ 
    theme_pubr()+
    rremove("legend.title")+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"),legend.position = c(0.92, 0.85))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +font("legend.text",size = 15)+
    theme(legend.position = "none")+
  labs(title = "Average body weight measurements")+
    theme(axis.title.x=element_blank())+
   stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="red", fill="red") +
  facet_grid(~Sex)

body_weight_violin_overall




```









<!-- # plots (fish length) for tanks -->

<!-- ```{r, echo = FALSE} -->
<!-- Summary_Length <- summarySE(Weight_Length_Data, measurevar="Fish_Length_cm", groupvars=c("Week","Group", "Sex")) -->

<!-- # So error bars aren't overlapping, we can use this: -->
<!-- pd <- position_dodge(0.1) # move them .05 to the left and right -->

<!-- plot_fish_length_tanks <- ggplot(Summary_Length, aes(x=Week, y=Fish_Length_cm, colour=Group)) +  -->
<!--   geom_errorbar(aes(ymin=Fish_Length_cm-se, ymax=Fish_Length_cm+se),colour="black", width=.1, position=pd) + -->
<!--   geom_line(position=pd) + -->
<!--   geom_point(position=pd)+ -->
<!--   labs(title = "Obesogenic vs. Control Diet", -->
<!--               subtitle = "Fish lengths after 22 weeks") + -->
<!--   facet_grid(~Sex) -->


<!-- plot_fish_length_tanks -->


<!-- body_length_violin <-   -->
<!--   ggplot(data = Weight_Length_Data,aes(x = Group, y = Fish_Length_cm, fill = Group))+ -->
<!--     scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+  -->
<!--     geom_violin(alpha=0.4, position = position_dodge(width = .75),size=1,color="black")+ -->
<!--     geom_boxplot(notch = TRUE,  outlier.size = -1, color="black",lwd=1.2, alpha = 0.7)+  -->
<!--     geom_point( shape = 21,size=2, position = position_jitterdodge(), color="black",alpha=1)+  -->
<!--     theme_pubr()+ -->
<!--     rremove("legend.title")+ -->
<!--     theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"),legend.position = c(0.92, 0.85))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +font("legend.text",size = 15)+ -->
<!--     theme(legend.position = "none")+ -->
<!--     theme(axis.title.x=element_blank())+ -->
<!--   facet_grid(~Sex) -->
<!-- body_length_violin -->
<!-- ``` -->

<!-- #Summary (BMI) -->

<!-- ```{r, echo = FALSE} -->

<!-- Summary_BMI <- summarySE(Weight_Length_Data, measurevar="BMI", groupvars=c("Week","Group", "Sex")) -->


<!-- plot_bmi <- ggplot(Summary_BMI, aes(x=Week, y=BMI, colour=Group)) +  -->
<!--   geom_errorbar(aes(ymin=BMI-se, ymax=BMI+se), width=.1,colour="black", position=pd) + -->
<!--   geom_line(position=pd) + -->
<!--   labs(title = "Obesogenic vs. Control Diet", -->
<!--               subtitle = "Fish BMI after 22 weeks (g/cm2)")+ -->
<!--   facet_grid(~Sex) -->



<!-- plot_bmi -->


<!-- ``` -->




```{r}
#Making scatterplot

Scatterplot <- ggplot(Weight_Length_Data, aes(Week, Weight.g., colour = Group)) +
  geom_jitter() +
  theme_bw() +
  facet_grid(~Sex) +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), aes(fill = Group)) #try different formulas and compare against each other
Scatterplot
```

