---
title: "Anxiety"
author: "Hamza"
date: "11/02/2020"
output: html_document
---

### Loading packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)


# Load custom functions
source("../Scripts/functions_learning.R")
source("../Scripts/functions_repeatability.R")
```


### Import Data and models
```{r, include=FALSE}
Anxiety_Joined <- read_xlsx("../Data/Anxiety/Anxiety_Data.xlsx")

load("../Models/Control_Tot_Dist.Rdata")
load("../Models/Treatment_Tot_Dist.Rdata")
load("../Models/within_between_tot_dist_control.Rdata")
load("../Models/within_between_tot_dist_treatment.Rdata")
load("../Models/Control_low_dur.Rdata")
load("../Models/Treatment_low_dur.Rdata")
load("../Models/within_between_low_dur_control.Rdata")
load("../Models/within_between_low_dur_treatment.Rdata")
load("../Models/Control_mid_dur.Rdata")
load("../Models/Treatment_mid_dur.Rdata")
load("../Models/within_between_mid_dur_control.Rdata")
load("../Models/within_between_mid_dur_treatment.Rdata")
load("../Models/Control_high_dur.Rdata")
load("../Models/Treatment_high_dur.Rdata")
load("../Models/within_between_high_dur_control.Rdata")
load("../Models/within_between_high_dur_treatment.Rdata")
load("../Models/Control_freezing_dur.Rdata")
load("../Models/Treatment_freezing_dur.Rdata")
load("../Models/within_between_freezing_dur_control.Rdata")
load("../Models/within_between_freezing_dur_treatment.Rdata")
load("../Models/Control_latency_high.Rdata")
load("../Models/Treatment_latency_high.Rdata")
load("../Models/within_between_latency_high_control.Rdata")
load("../Models/within_between_latency_high_treatment.Rdata")
load("../Models/Control_freq_high.Rdata")
load("../Models/Treatment_freq_high.Rdata")
load("../Models/within_between_freq_high_control.Rdata")
load("../Models/within_between_freq_high_treatment.Rdata")
```

### Examine Data

```{r, include=FALSE}

str(Anxiety_Joined)


#Convert characters into factors

Anxiety_Joined$Sex <- as.factor(Anxiety_Joined$Sex)
Anxiety_Joined$Group <- as.factor(Anxiety_Joined$Group)
Anxiety_Joined$Fish_ID <- as.factor(Anxiety_Joined$Fish_ID)
Anxiety_Joined$Day <- as.factor(Anxiety_Joined$Day)
Anxiety_Joined$Tank <- as.factor(Anxiety_Joined$Tank)

#Subsetting into control and treatment

Anxiety_Control <- subset(Anxiety_Joined, Anxiety_Joined$Group == "Control") 
Anxiety_Treatment <- subset(Anxiety_Joined, Anxiety_Joined$Group == "Treatment") 
```


### MAIN ANALYSIS FOR ALL BEHAVIORAL PARAMETERS
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITY OF CONTROL AND TREATMENT GROUP
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT GROUPS

THESE STEPS ARE REPEATED FOR ALL BEHAVIORAL PARAMETERS, REFER TO THE FIRST BEHAVIORAL PARAMETER FOR COMMENTS AND REFERENCE 

NEED TO EDIT COMMENTS !


# Total distance travelled
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_Tot_Dist <- lmer(tot_dist ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_Tot_Dist)#mixed model 
hist(residuals(Model_Tot_Dist)) #histogram of residuals to check for normal distribution (easiest way to check assumption of normality)


# #Calculating repeatabilities using custom made functions
# rpt_tot_dist(Anxiety_Control) -> Control_Tot_Dist 
# Control_Tot_Dist
# rpt_tot_dist(Anxiety_Treatment) -> Treatment_Tot_Dist 
# Treatment_Tot_Dist
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_tot_dist(Anxiety_Control) -> within_between_tot_dist_control 
# within_between_tot_dist_control
# rpt_within_between_tot_dist(Anxiety_Treatment)-> within_between_tot_dist_treatment 
# within_between_tot_dist_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_tot_dist_boot <- unlist_rptr(Control_Tot_Dist) #unlisting 
Treatment_tot_dist_boot <- unlist_rptr(Treatment_Tot_Dist) #unlisting 
Tot_dist_diff <- difference_boot(Control_tot_dist_boot,Treatment_tot_dist_boot) #calculating the difference
q1 <- quantiles_diff_boot(Tot_dist_diff) #obtaining 95% CI
m1 <- mean(Tot_dist_diff) #Obtaining mean

q1
m1

# Calculating difference in variance between 
Model_Tot_Dist1 <- lme(tot_dist ~ Group*Sex + scale(Water_ID, scale = FALSE), random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_Tot_Dist1) 
tab_model(Model_Tot_Dist1)
Model_Tot_Dist2 <- lme(tot_dist ~ Group*Sex + scale(Water_ID, scale = FALSE), random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Tot_Dist2)
anova(Model_Tot_Dist1, Model_Tot_Dist2) #calculating difference between two models to find difference in variance
```


# Time spent in low zone
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_low_dur <- lmer(low_dur ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined)
summary(Model_low_dur)#mixed model 
tab_model(Model_low_dur)
hist(residuals(Model_low_dur)) #histogram of residuals reveals a transformation is needed ?

# #Calculating repeatabilities using custom made functions
# rpt_low_dur(Anxiety_Control) -> Control_low_dur 
# Control_low_dur 
# rpt_low_dur(Anxiety_Treatment) -> Treatment_low_dur 
# Treatment_low_dur
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_low_dur(Anxiety_Control) -> within_between_low_dur_control
# within_between_low_dur_control
# rpt_within_between_low_dur(Anxiety_Treatment)-> within_between_low_dur_treatment 
# within_between_low_dur_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_low_dur_boot <- unlist_rptr(Control_low_dur) #unlisting from the 
Treatment_low_dur_boot <- unlist_rptr(Treatment_low_dur) #unlisting from the 
low_dur_diff <- difference_boot(Control_low_dur_boot,Treatment_low_dur_boot) #calculating the difference
q2 <- quantiles_diff_boot(low_dur_diff) #obtaining 95% CI
m2 <- mean(low_dur_diff) #Obtaining mean

q2
m2

# Calculating difference in variance between  and  
Model_low_dur1 <- lme(low_dur ~ Group*Sex + scale(Water_ID, scale = FALSE), random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_low_dur1)
contrasts_low_dur <- emmeans(Model_low_dur1, c("Group", "Sex"))
pairs(contrasts_low_dur)
tab_model(Model_low_dur1)
Model_low_dur2 <- lme(low_dur ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_low_dur2)
anova(Model_low_dur1, Model_low_dur2) #calculating difference between two models to find difference in variance
```


# Time spent in mid zone
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_mid_dur <- lmer(mid_dur ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined)
summary(Model_mid_dur)#mixed model 
tab_model(Model_mid_dur)
hist(residuals(Model_mid_dur)) #histogram of residuals - transformation ?


# #Calculating repeatabilities using custom made functions
# rpt_mid_dur(Anxiety_Control) -> Control_mid_dur 
# Control_mid_dur
# rpt_mid_dur(Anxiety_Treatment) -> Treatment_mid_dur 
# Treatment_mid_dur
# 
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_mid_dur(Anxiety_Control) -> within_between_mid_dur_control
# within_between_mid_dur_control
# rpt_within_between_mid_dur(Anxiety_Treatment)-> within_between_mid_dur_treatment
# within_between_mid_dur_treatment


#Obtaining differences between repeatabilities using custom made functions
Control_mid_dur_boot <- unlist_rptr(Control_mid_dur) #unlisting from the 
Treatment_mid_dur_boot <- unlist_rptr(Treatment_mid_dur) #unlisting from the 
mid_dur_diff <- difference_boot(Control_mid_dur_boot,Treatment_mid_dur_boot) #calculating the difference
q3 <- quantiles_diff_boot(mid_dur_diff) #obtaining 95% CI
m3 <- mean(mid_dur_diff) #Obtaining mean

q3
m3

# Calculating difference in variance between  and  
Model_mid_dur1 <- lme(mid_dur ~ Group*Sex + scale(Water_ID, scale = FALSE), random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_mid_dur1)
Model_mid_dur2 <- lme(mid_dur ~ Group*Sex + scale(Water_ID, scale = FALSE), random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_mid_dur2)
anova(Model_mid_dur1, Model_mid_dur2) #calculating difference between two models to find difference in variance
```


# Time spent in high zone
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_high_dur <- lmer(high_dur ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
tab_model(Model_high_dur)
hist(residuals(Model_high_dur)) #histogram of residuals reveals transformation required

Model_high_dur0 <- lmer(log(high_dur+1) ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
summary(Model_high_dur0)
tab_model(Model_high_dur0)
hist(residuals(Model_high_dur0)) #better normal distribution

# #Calculating repeatabilities using custom made functions
# rpt_high_dur2(Anxiety_Control) -> Control_high_dur 
# Control_high_dur
# rpt_high_dur2(Anxiety_Treatment) -> Treatment_high_dur 
# Treatment_high_dur
# 
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_high_dur2(Anxiety_Control) -> within_between_high_dur_control 
# within_between_high_dur_control
# rpt_within_between_high_dur2(Anxiety_Treatment)-> within_between_high_dur_treatment 
# within_between_high_dur_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_high_dur_boot <- unlist_rptr(Control_high_dur) #unlisting from the 
Treatment_high_dur_boot <- unlist_rptr(Treatment_high_dur) #unlisting from the 
high_dur_diff <- difference_boot(Control_high_dur_boot,Treatment_high_dur_boot) #calculating the difference
q4 <- quantiles_diff_boot(high_dur_diff) #obtaining 95% CI
m4 <- mean(high_dur_diff) #Obtaining mean

q4
m4

# Calculating difference in variance between  and  
Model_high_dur1 <- lme(log(high_dur+1) ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_high_dur1)
Model_high_dur2 <- lme(log(high_dur+1) ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_high_dur2)
anova(Model_high_dur1, Model_high_dur2) #calculating difference between two models to find difference in variance
```

# Time spent freezing
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_freezing_dur <- lmer(freezing_dur ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
tab_model(Model_freezing_dur)
hist(residuals(Model_freezing_dur)) #histogram of residuals reveals a transformation is required

Model_freezing_dur0 <- lmer(log(freezing_dur+1) ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
tab_model(Model_freezing_dur0)
hist(residuals(Model_freezing_dur0))


# #Calculating repeatabilities using custom made functions
# rpt_freezing_dur(Anxiety_Control) -> Control_freezing_dur 
# Control_freezing_dur
# rpt_freezing_dur(Anxiety_Treatment) -> Treatment_freezing_dur 
# Treatment_freezing_dur
# 
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_freezing_dur(Anxiety_Control) -> within_between_freezing_dur_control 
# within_between_freezing_dur_control
# rpt_within_between_freezing_dur(Anxiety_Treatment)-> within_between_freezing_dur_treatment 
# within_between_freezing_dur_treatment


#Obtaining differences between repeatabilities using custom made functions
Control_freezing_dur_boot <- unlist_rptr(Control_freezing_dur) #unlisting from the 
Treatment_freezing_dur_boot <- unlist_rptr(Treatment_freezing_dur) #unlisting from the 
freezing_dur_diff <- difference_boot(Control_freezing_dur_boot,Treatment_freezing_dur_boot) #calculating the difference
q5 <- quantiles_diff_boot(freezing_dur_diff) #obtaining 95% CI
m5 <- mean(freezing_dur_diff) #Obtaining mean

q5
m5

# Calculating difference in variance between  and  
Model_freezing_dur1 <- lme(log(freezing_dur+1) ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_freezing_dur1)
Model_freezing_dur2 <- lme(log(freezing_dur+1) ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_freezing_dur2)
anova(Model_freezing_dur1, Model_freezing_dur2) #calculating difference between two models to find difference in variance
```

# Latency to high
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_latency_high <- lmer(latency_high ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
tab_model(Model_latency_high)
hist(residuals(Model_latency_high)) #histogram of residuals to check for normal distribution (easiest way to check assumption of normality)

# 
# #Calculating repeatabilities using custom made functions
# rpt_latency(Anxiety_Control) -> Control_latency_high
# Control_latency_high
# rpt_latency(Anxiety_Treatment) -> Treatment_latency_high 
# Treatment_latency_high
# 
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_latency(Anxiety_Control) -> within_between_latency_high_control
# within_between_latency_high_control
# rpt_within_between_latency(Anxiety_Treatment)-> within_between_latency_high_treatment 
# within_between_latency_high_treatment


#Obtaining differences between repeatabilities using custom made functions
Control_latency_high_boot <- unlist_rptr(Control_latency_high) #unlisting from the 
Treatment_latency_high_boot <- unlist_rptr(Treatment_latency_high) #unlisting from the 
latency_high_diff <- difference_boot(Control_latency_high_boot,Treatment_latency_high_boot) #calculating the difference
q6 <- quantiles_diff_boot(latency_high_diff) #obtaining 95% CI
m6 <- mean(latency_high_diff) #Obtaining mean

q6
m6

# Calculating difference in variance between  and  
Model_latency_high1 <- lme(latency_high ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_latency_high1)
Model_latency_high2 <- lme(latency_high ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_latency_high2)
anova(Model_latency_high1, Model_latency_high2) #calculating difference between two models to find difference in variance
```


# Entries to high zone
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_freq_high <- lmer(freq_high ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined) #mixed model 
hist(residuals(Model_freq_high)) #histogram of residuals reveals a transformation is required

Model_freq_high0 <- lmer(sqrt(freq_high) ~ Group*Sex + scale(Water_ID, scale = FALSE) + (1 | Fish_ID), data = Anxiety_Joined)
summary(Model_freq_high0)
tab_model(Model_freq_high0)#mixed model 
hist(residuals(Model_freq_high0))

# #Calculating repeatabilities using custom made functions
# rpt_freq(Anxiety_Control) -> Control_freq_high 
# Control_freq_high
# rpt_freq(Anxiety_Treatment) -> Treatment_freq_high 
# Treatment_freq_high
# 
# 
# #Obtaining within-individual and between-individual variance for total distace 
# 
# rpt_within_between_freq_high(Anxiety_Control) -> within_between_freq_high_control 
# within_between_freq_high_control
# rpt_within_between_freq_high(Anxiety_Treatment)-> within_between_freq_high_treatment 
# within_between_freq_high_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_freq_high_boot <- unlist_rptr(Control_freq_high) #unlisting from the 
Treatment_freq_high_boot <- unlist_rptr(Treatment_freq_high) #unlisting from the 
freq_high_diff <- difference_boot(Control_freq_high_boot,Treatment_freq_high_boot) #calculating the difference
q7 <- quantiles_diff_boot(freq_high_diff) #obtaining 95% CI
m7 <- mean(freq_high_diff) #Obtaining mean

q7
m7

# Calculating difference in variance between  and  
Model_freq_high1 <- lme(sqrt(freq_high) ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Anxiety_Joined, na.action=na.exclude) #mixed model without variance structure
summary(Model_freq_high1)
Model_freq_high2 <- lme(sqrt(freq_high) ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Anxiety_Joined, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_freq_high2)
anova(Model_freq_high1, Model_freq_high2) #calculating difference between two models to find difference in variance
```

<!-- #Running code all at once for repeatabilities -->
<!-- ```{r} -->
<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_tot_dist(Anxiety_Control) -> Control_Tot_Dist  -->
<!-- Control_Tot_Dist -->
<!-- save(Control_Tot_Dist, file = "../Models/Control_Tot_Dist.Rdata") -->
<!-- rpt_tot_dist(Anxiety_Treatment) -> Treatment_Tot_Dist  -->
<!-- save(Treatment_Tot_Dist, file = "../Models/Treatment_Tot_Dist.Rdata") -->
<!-- Treatment_Tot_Dist -->

<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_tot_dist(Anxiety_Control) -> within_between_tot_dist_control  -->
<!-- save(within_between_tot_dist_control, file = "../Models/within_between_tot_dist_control.Rdata") -->
<!-- within_between_tot_dist_control -->
<!-- rpt_within_between_tot_dist(Anxiety_Treatment)-> within_between_tot_dist_treatment  -->
<!-- save(within_between_tot_dist_treatment, file = "../Models/within_between_tot_dist_treatment.Rdata") -->
<!-- within_between_tot_dist_treatment -->

<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_low_dur(Anxiety_Control) -> Control_low_dur  -->
<!-- save(Control_low_dur, file = "../Models/Control_low_dur.Rdata") -->
<!-- Control_low_dur  -->
<!-- rpt_low_dur(Anxiety_Treatment) -> Treatment_low_dur  -->
<!-- save(Treatment_low_dur, file = "../Models/Treatment_low_dur.Rdata") -->
<!-- Treatment_low_dur -->

<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_low_dur(Anxiety_Control) -> within_between_low_dur_control -->
<!-- save(within_between_low_dur_control, file = "../Models/within_between_low_dur_control.Rdata") -->
<!-- within_between_low_dur_control -->
<!-- rpt_within_between_low_dur(Anxiety_Treatment)-> within_between_low_dur_treatment  -->
<!-- save(within_between_low_dur_treatment, file = "../Models/within_between_low_dur_treatment.Rdata") -->
<!-- within_between_low_dur_treatment -->

<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_mid_dur(Anxiety_Control) -> Control_mid_dur  -->
<!-- save(Control_mid_dur, file = "../Models/Control_mid_dur.Rdata") -->
<!-- Control_mid_dur -->
<!-- rpt_mid_dur(Anxiety_Treatment) -> Treatment_mid_dur  -->
<!-- save(Treatment_mid_dur, file = "../Models/Treatment_mid_dur.Rdata") -->
<!-- Treatment_mid_dur -->


<!-- #Obtaining within-individual and between-individual variance   -->

<!-- rpt_within_between_mid_dur(Anxiety_Control) -> within_between_mid_dur_control -->
<!-- save(within_between_mid_dur_control, file = "../Models/within_between_mid_dur_control.Rdata") -->
<!-- within_between_mid_dur_control -->
<!-- rpt_within_between_mid_dur(Anxiety_Treatment)-> within_between_mid_dur_treatment -->
<!-- save(within_between_mid_dur_treatment, file = "../Models/within_between_mid_dur_treatment.Rdata") -->
<!-- within_between_mid_dur_treatment -->

<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_high_dur2(Anxiety_Control) -> Control_high_dur  -->
<!-- save(Control_high_dur, file = "../Models/Control_high_dur.Rdata") -->
<!-- Control_high_dur -->
<!-- rpt_high_dur2(Anxiety_Treatment) -> Treatment_high_dur  -->
<!-- save(Treatment_high_dur, file = "../Models/Treatment_high_dur.Rdata") -->
<!-- Treatment_high_dur -->


<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_high_dur2(Anxiety_Control) -> within_between_high_dur_control  -->
<!-- save(within_between_high_dur_control, file = "../Models/within_between_high_dur_control.Rdata") -->
<!-- within_between_high_dur_control -->
<!-- rpt_within_between_high_dur2(Anxiety_Treatment)-> within_between_high_dur_treatment  -->
<!-- save(within_between_high_dur_treatment, file = "../Models/within_between_high_dur_treatment.Rdata") -->
<!-- within_between_high_dur_treatment -->

<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_freezing_dur(Anxiety_Control) -> Control_freezing_dur  -->
<!-- save(Control_freezing_dur, file = "../Models/Control_freezing_dur.Rdata") -->
<!-- Control_freezing_dur -->
<!-- rpt_freezing_dur(Anxiety_Treatment) -> Treatment_freezing_dur -->
<!-- save(Treatment_freezing_dur, file = "../Models/Treatment_freezing_dur.Rdata") -->
<!-- Treatment_freezing_dur -->


<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_freezing_dur(Anxiety_Control) -> within_between_freezing_dur_control  -->
<!-- save(within_between_freezing_dur_control, file = "../Models/within_between_freezing_dur_control.Rdata") -->
<!-- within_between_freezing_dur_control -->
<!-- rpt_within_between_freezing_dur(Anxiety_Treatment)-> within_between_freezing_dur_treatment  -->
<!-- save(within_between_freezing_dur_treatment, file = "../Models/within_between_freezing_dur_treatment.Rdata") -->
<!-- within_between_freezing_dur_treatment -->


<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_latency(Anxiety_Control) -> Control_latency_high -->
<!-- save(Control_latency_high, file = "../Models/Control_latency_high.Rdata") -->
<!-- Control_latency_high -->
<!-- rpt_latency(Anxiety_Treatment) -> Treatment_latency_high  -->
<!-- save(Treatment_latency_high, file = "../Models/Treatment_latency_high.Rdata") -->
<!-- Treatment_latency_high -->


<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_latency(Anxiety_Control) -> within_between_latency_high_control -->
<!-- save(within_between_latency_high_control, file = "../Models/within_between_latency_high_control.Rdata") -->
<!-- within_between_latency_high_control -->
<!-- rpt_within_between_latency(Anxiety_Treatment)-> within_between_latency_high_treatment  -->
<!-- save(within_between_latency_high_treatment, file = "../Models/within_between_latency_high_treatment.Rdata") -->
<!-- within_between_latency_high_treatment -->

<!-- #Calculating repeatabilities using custom made functions -->
<!-- rpt_freq(Anxiety_Control) -> Control_freq_high  -->
<!-- save(Control_freq_high, file = "../Models/Control_freq_high.Rdata") -->
<!-- Control_freq_high -->
<!-- rpt_freq(Anxiety_Treatment) -> Treatment_freq_high  -->
<!-- save(Treatment_freq_high, file = "../Models/Treatment_freq_high.Rdata") -->
<!-- Treatment_freq_high -->


<!-- #Obtaining within-individual and between-individual variance  -->

<!-- rpt_within_between_freq_high(Anxiety_Control) -> within_between_freq_high_control  -->
<!-- save(within_between_freq_high_control, file = "../Models/within_between_freq_high_control.Rdata") -->
<!-- within_between_freq_high_control -->
<!-- rpt_within_between_freq_high(Anxiety_Treatment)-> within_between_freq_high_treatment  -->
<!-- save(within_between_freq_high_treatment, file = "../Models/within_between_freq_high_treatment.Rdata") -->
<!-- within_between_freq_high_treatment -->
<!-- ``` -->

