---
title: "Anxiety Sex Analysis F0"
author: "Hamza"
date: "23/10/2020"
output: html_document
---

### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)

# Load custom functions
source("../Scripts/functions_repeatability.R") #load custom functions
```

#Subset data by sex; load models
```{r}
#Subset by sex
Anxiety_Control_Male <- subset(Anxiety_Control, Anxiety_Control$Sex == "male")
Anxiety_Control_Female <- subset(Anxiety_Control, Anxiety_Control$Sex == "female")
Anxiety_Treatment_Male <- subset(Anxiety_Treatment, Anxiety_Treatment$Sex == "male")
Anxiety_Treatment_Female <- subset(Anxiety_Treatment, Anxiety_Treatment$Sex == "female")

#Loading rpt models

load("../Models/Control_Tot_Dist_Male.Rdata")
load("../Models/Treatment_Tot_Dist_Male.Rdata")
load("../Models/Control_Tot_Dist_Female.Rdata")
load("../Models/Treatment_Tot_Dist_Female.Rdata")
load("../Models/Control_low_dur_Male.Rdata")
load("../Models/Treatment_low_dur_Male.Rdata")
load("../Models/Control_low_dur_Female.Rdata")
load("../Models/Treatment_low_dur_Female.Rdata")
load("../Models/Control_mid_dur_Male.Rdata")
load("../Models/Treatment_mid_dur_Male.Rdata")
load("../Models/Control_mid_dur_Female.Rdata")
load("../Models/Treatment_mid_dur_Female.Rdata")
load("../Models/Control_high_dur_Male.Rdata")
load("../Models/Treatment_high_dur_Male.Rdata")
load("../Models/Control_high_dur_Female.Rdata")
load("../Models/Treatment_high_dur_Female.Rdata")
load("../Models/Control_freezing_dur_Male.Rdata")
load("../Models/Treatment_freezing_dur_Male.Rdata")
load("../Models/Control_freezing_dur_Female.Rdata")
load("../Models/Treatment_freezing_dur_Female.Rdata")
load("../Models/Control_latency_high_Male.Rdata")
load("../Models/Treatment_latency_high_Male.Rdata")
load("../Models/Control_latency_high_Female.Rdata")
load("../Models/Treatment_latency_high_Female.Rdata")
load("../Models/Control_freq_high_Male.Rdata")
load("../Models/Treatment_freq_high_Male.Rdata")
load("../Models/Control_freq_high_Female.Rdata")
load("../Models/Treatment_freq_high_Female.Rdata")


```

### MAIN ANALYSIS FOR ALL BEHAVIORAL PARAMETERS BY SEX AND TANK
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS FOR EACH SEX IN EACH TANK SEPARATELY (USING SUBSETS) AND THEN WITH BOTH DATA COMBINED FOR EACH TANK
3) CALCULATING DIFFERENCES BETWEEN MALE AND FEMALE REPEATABILITIES IN EACH TANK

THESE STEPS ARE REPEATED FOR ALL BEHAVIORAL PARAMETERS, REFER TO THE FIRST BEHAVIORAL PARAMETER FOR COMMENTS AND REFERENCE 

### Total distance travelled
```{r}
#Checking normality assumption
Model_Tot_Dist_sex <- lmer(tot_dist ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_Tot_Dist)
hist(residuals(Model_Tot_Dist_sex))

# #Repeatability analysis males
# rpt_tot_dist(Anxiety_Control_Male) -> Control_Tot_Dist_Male 
# Control_Tot_Dist_Male
# rpt_tot_dist(Anxiety_Treatment_Male) -> Treatment_Tot_Dist_Male 
# Treatment_Tot_Dist_Male
# 
# #Repeatability analysis females
# rpt_tot_dist(Anxiety_Control_Female) -> Control_Tot_Dist_Female 
# Control_Tot_Dist_Female
# rpt_tot_dist(Anxiety_Treatment_Female) -> Treatment_Tot_Dist_Female
# Treatment_Tot_Dist_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_Tot_Dist_Female_boot<-unlist(Control_Tot_Dist_Female$R_boot) #unlisting boots from repeatability analysis
Control_Tot_Dist_Male_boot<-unlist(Control_Tot_Dist_Male$R_boot)

Diff_boot_Tot_Dist_Control <- Control_Tot_Dist_Female_boot - Control_Tot_Dist_Male_boot #getting difference from boots


q_tot_control <- quantile(Diff_boot_Tot_Dist_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_tot_Control <- mean(Diff_boot_Tot_Dist_Control) #Obtaining mean

mean_tot_Control
q_tot_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_Tot_Dist_Female_boot<-unlist(Treatment_Tot_Dist_Female$R_boot)
Treatment_Tot_Dist_Male_boot<-unlist(Treatment_Tot_Dist_Male$R_boot)

Diff_boot_Tot_Dist_Treatment <- Treatment_Tot_Dist_Male_boot - Treatment_Tot_Dist_Female_boot

q_tot_Treatment <- quantile(Diff_boot_Tot_Dist_Treatment, c(0.025, 0.975)) 
mean_tot_Treatment <- mean(Diff_boot_Tot_Dist_Treatment)

mean_tot_Treatment
q_tot_Treatment
```


### Time spent in low zone
```{r}
#Checking normality assumption
Model_low_dur_sex <- lmer(low_dur ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_low_dur)
hist(residuals(Model_low_dur_sex))

# #Repeatability analysis males
# rpt_low_dur(Anxiety_Control_Male) -> Control_low_dur_Male 
# Control_low_dur_Male
# rpt_low_dur(Anxiety_Treatment_Male) -> Treatment_low_dur_Male 
# Treatment_low_dur_Male
# 
# #Repeatability analysis females
# rpt_low_dur(Anxiety_Control_Female) -> Control_low_dur_Female 
# Control_low_dur_Female
# rpt_low_dur(Anxiety_Treatment_Female) -> Treatment_low_dur_Female
# Treatment_low_dur_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_low_dur_Female_boot<-unlist(Control_low_dur_Female$R_boot) #unlisting boots from repeatability analysis
Control_low_dur_Male_boot<-unlist(Control_low_dur_Male$R_boot)

Diff_boot_low_dur_Control <- Control_low_dur_Female_boot - Control_low_dur_Male_boot #getting difference from boots


q_low_dur_control <- quantile(Diff_boot_low_dur_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_low_dur_Control <- mean(Diff_boot_low_dur_Control) #Obtaining mean

mean_low_dur_Control
q_low_dur_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_low_dur_Female_boot<-unlist(Treatment_low_dur_Female$R_boot)
Treatment_low_dur_Male_boot<-unlist(Treatment_low_dur_Male$R_boot)

Diff_boot_low_dur_Treatment <- Treatment_low_dur_Female_boot - Treatment_low_dur_Male_boot

q_low_dur_Treatment <- quantile(Diff_boot_low_dur_Treatment, c(0.025, 0.975)) 
mean_low_dur_Treatment <- mean(Diff_boot_low_dur_Treatment)

mean_low_dur_Treatment
q_low_dur_Treatment
```

### Time spent in mid zone
```{r}
#Checking normality assumption
Model_mid_dur_sex <- lmer(mid_dur ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_mid_dur)
hist(residuals(Model_mid_dur_sex))

# #Repeatability analysis males
# rpt_mid_dur(Anxiety_Control_Male) -> Control_mid_dur_Male 
# Control_mid_dur_Male
# rpt_mid_dur(Anxiety_Treatment_Male) -> Treatment_mid_dur_Male 
# Treatment_mid_dur_Male
# 
# #Repeatability analysis females
# rpt_mid_dur(Anxiety_Control_Female) -> Control_mid_dur_Female 
# Control_mid_dur_Female
# rpt_mid_dur(Anxiety_Treatment_Female) -> Treatment_mid_dur_Female
# Treatment_mid_dur_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_mid_dur_Female_boot<-unlist(Control_mid_dur_Female$R_boot) #unlisting boots from repeatability analysis
Control_mid_dur_Male_boot<-unlist(Control_mid_dur_Male$R_boot)

Diff_boot_mid_dur_Control <- Control_mid_dur_Female_boot - Control_mid_dur_Male_boot #getting difference from boots


q_mid_dur_control <- quantile(Diff_boot_mid_dur_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_mid_dur_control <- mean(Diff_boot_mid_dur_Control) #Obtaining mean

mean_mid_dur_control
q_mid_dur_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_mid_dur_Female_boot<-unlist(Treatment_mid_dur_Female$R_boot)
Treatment_mid_dur_Male_boot<-unlist(Treatment_mid_dur_Male$R_boot)

Diff_boot_mid_dur_Treatment <- Treatment_mid_dur_Female_boot - Treatment_mid_dur_Male_boot

q_mid_dur_Treatment <- quantile(Diff_boot_mid_dur_Treatment, c(0.025, 0.975)) 
mean_mid_dur_Treatment <- mean(Diff_boot_mid_dur_Treatment)

mean_mid_dur_Treatment
q_mid_dur_Treatment
```

### Time spent in high zone
```{r}
#Checking normality assumption
Model_high_dur_sex <- lmer(sqrt(high_dur) ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_high_dur)
hist(residuals(Model_high_dur_sex))

# #Repeatability analysis males
# rpt_high_dur(Anxiety_Control_Male) -> Control_high_dur_Male 
# Control_high_dur_Male
# rpt_high_dur(Anxiety_Treatment_Male) -> Treatment_high_dur_Male 
# Treatment_high_dur_Male
# 
# #Repeatability analysis females
# rpt_high_dur(Anxiety_Control_Female) -> Control_high_dur_Female 
# Control_high_dur_Female
# rpt_high_dur(Anxiety_Treatment_Female) -> Treatment_high_dur_Female
# Treatment_high_dur_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_high_dur_Female_boot<-unlist(Control_high_dur_Female$R_boot) #unlisting boots from repeatability analysis
Control_high_dur_Male_boot<-unlist(Control_high_dur_Male$R_boot)

Diff_boot_high_dur_Control <- Control_high_dur_Male_boot - Control_high_dur_Female_boot #getting difference from boots


q_high_dur_control <- quantile(Diff_boot_high_dur_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_high_dur_control <- mean(Diff_boot_high_dur_Control) #Obtaining mean

mean_high_dur_control
q_high_dur_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_high_dur_Female_boot<-unlist(Treatment_high_dur_Female$R_boot)
Treatment_high_dur_Male_boot<-unlist(Treatment_high_dur_Male$R_boot)

Diff_boot_high_dur_Treatment <- Treatment_high_dur_Female_boot - Treatment_high_dur_Male_boot

q_high_dur_Treatment <- quantile(Diff_boot_high_dur_Treatment, c(0.025, 0.975)) 
mean_high_dur_Treatment <- mean(Diff_boot_high_dur_Treatment)

mean_high_dur_Treatment
q_high_dur_Treatment
```


### Time spent freezing
```{r}
#Checking normality assumption
Model_freezing_dur_sex <- lmer(log(freezing_dur+1) ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_freezing_dur)
hist(residuals(Model_freezing_dur_sex))

# #Repeatability analysis males
# rpt_freezing_dur(Anxiety_Control_Male) -> Control_freezing_dur_Male 
# Control_freezing_dur_Male
# rpt_freezing_dur(Anxiety_Treatment_Male) -> Treatment_freezing_dur_Male 
# Treatment_freezing_dur_Male
# 
# #Repeatability analysis females
# rpt_freezing_dur(Anxiety_Control_Female) -> Control_freezing_dur_Female 
# Control_freezing_dur_Female
# rpt_freezing_dur(Anxiety_Treatment_Female) -> Treatment_freezing_dur_Female
# Treatment_freezing_dur_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_freezing_dur_Female_boot<-unlist(Control_freezing_dur_Female$R_boot) #unlisting boots from repeatability analysis
Control_freezing_dur_Male_boot<-unlist(Control_freezing_dur_Male$R_boot)

Diff_boot_freezing_dur_Control <- Control_freezing_dur_Female_boot - Control_freezing_dur_Male_boot #getting difference from boots


q_freezing_dur_control <- quantile(Diff_boot_freezing_dur_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_freezing_dur_control <- mean(Diff_boot_freezing_dur_Control) #Obtaining mean

mean_freezing_dur_control
q_freezing_dur_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_freezing_dur_Female_boot<-unlist(Treatment_freezing_dur_Female$R_boot)
Treatment_freezing_dur_Male_boot<-unlist(Treatment_freezing_dur_Male$R_boot)

Diff_boot_freezing_dur_Treatment <- Treatment_freezing_dur_Male_boot - Treatment_freezing_dur_Female_boot

q_freezing_dur_Treatment <- quantile(Diff_boot_freezing_dur_Treatment, c(0.025, 0.975)) 
mean_freezing_dur_Treatment <- mean(Diff_boot_freezing_dur_Treatment)

mean_freezing_dur_Treatment
q_freezing_dur_Treatment
```


### Latency to high
```{r}
#Checking normality assumption
Model_latency_high_sex <- lmer(latency_high ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_latency_high)
hist(residuals(Model_latency_high_sex))

# #Repeatability analysis males
# rpt_latency(Anxiety_Control_Male) -> Control_latency_high_Male 
# Control_latency_high_Male
# rpt_latency(Anxiety_Treatment_Male) -> Treatment_latency_high_Male 
# Treatment_latency_high_Male
# 
# #Repeatability analysis females
# rpt_latency(Anxiety_Control_Female) -> Control_latency_high_Female 
# Control_latency_high_Female
# rpt_latency(Anxiety_Treatment_Female) -> Treatment_latency_high_Female
# Treatment_latency_high_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_latency_high_Female_boot<-unlist(Control_latency_high_Female$R_boot) #unlisting boots from repeatability analysis
Control_latency_high_Male_boot<-unlist(Control_latency_high_Male$R_boot)

Diff_boot_latency_high_Control <- Control_latency_high_Female_boot - Control_latency_high_Male_boot #getting difference from boots


q_latency_high_control <- quantile(Diff_boot_latency_high_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_latency_high_control <- mean(Diff_boot_latency_high_Control) #Obtaining mean

mean_latency_high_control
q_latency_high_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_latency_high_Female_boot<-unlist(Treatment_latency_high_Female$R_boot)
Treatment_latency_high_Male_boot<-unlist(Treatment_latency_high_Male$R_boot)

Diff_boot_latency_high_Treatment <- Treatment_latency_high_Female_boot - Treatment_latency_high_Male_boot

q_latency_high_Treatment <- quantile(Diff_boot_latency_high_Treatment, c(0.025, 0.975)) 
mean_latency_high_Treatment <- mean(Diff_boot_latency_high_Treatment)

mean_latency_high_Treatment
q_latency_high_Treatment
```

### Entries to high zone
```{r}
#Checking normality assumption
Model_freq_high_sex <- lmer(sqrt(freq_high) ~ Tank + Sex + (1 | Fish_ID), data = Anxiety_Joined)
tab_model(Model_freq_high)
hist(residuals(Model_freq_high_sex))

# #Repeatability analysis males
# rpt_freq(Anxiety_Control_Male) -> Control_freq_high_Male 
# Control_freq_high_Male
# rpt_freq(Anxiety_Treatment_Male) -> Treatment_freq_high_Male 
# Treatment_freq_high_Male
# 
# #Repeatability analysis females
# rpt_freq(Anxiety_Control_Female) -> Control_freq_high_Female 
# Control_freq_high_Female
# rpt_freq(Anxiety_Treatment_Female) -> Treatment_freq_high_Female
# Treatment_freq_high_Female



#Contrast analysis to calculate differences between males and females in the control group

Control_freq_high_Female_boot<-unlist(Control_freq_high_Female$R_boot) #unlisting boots from repeatability analysis
Control_freq_high_Male_boot<-unlist(Control_freq_high_Male$R_boot)

Diff_boot_freq_high_Control <- Control_freq_high_Female_boot - Control_freq_high_Male_boot #getting difference from boots


q_freq_high_control <- quantile(Diff_boot_freq_high_Control, c(0.025, 0.975)) #calculating quantiles at 2.5% and 97.5% (will become 95% CI)
mean_freq_high_control <- mean(Diff_boot_freq_high_Control) #Obtaining mean

mean_freq_high_control
q_freq_high_control

#Contrast analysis to calculate differences between males and females in the treatment group

Treatment_freq_high_Female_boot<-unlist(Treatment_freq_high_Female$R_boot)
Treatment_freq_high_Male_boot<-unlist(Treatment_freq_high_Male$R_boot)

Diff_boot_freq_high_Treatment <- Treatment_freq_high_Female_boot - Treatment_freq_high_Male_boot

q_freq_high_Treatment <- quantile(Diff_boot_freq_high_Treatment, c(0.025, 0.975)) 
mean_freq_high_Treatment <- mean(Diff_boot_freq_high_Treatment)

mean_freq_high_Treatment
q_freq_high_Treatment
```

<!-- Code to run everything at once -->
<!-- ```{r} -->
<!-- #Repeatability analysis males -->
<!-- rpt_tot_dist(Anxiety_Control_Male) -> Control_Tot_Dist_Male  -->
<!-- save(Control_Tot_Dist_Male, file = "../Models/Control_Tot_Dist_Male.Rdata") -->
<!-- Control_Tot_Dist_Male -->
<!-- rpt_tot_dist(Anxiety_Treatment_Male) -> Treatment_Tot_Dist_Male  -->
<!-- save(Treatment_Tot_Dist_Male, file = "../Models/Treatment_Tot_Dist_Male.Rdata") -->
<!-- Treatment_Tot_Dist_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_tot_dist(Anxiety_Control_Female) -> Control_Tot_Dist_Female  -->
<!-- Control_Tot_Dist_Female -->
<!-- save(Control_Tot_Dist_Female, file = "../Models/Control_Tot_Dist_Female.Rdata") -->
<!-- rpt_tot_dist(Anxiety_Treatment_Female) -> Treatment_Tot_Dist_Female -->
<!-- Treatment_Tot_Dist_Female -->
<!-- save(Treatment_Tot_Dist_Female, file = "../Models/Treatment_Tot_Dist_Female.Rdata") -->

<!-- #Repeatability analysis males -->
<!-- rpt_low_dur(Anxiety_Control_Male) -> Control_low_dur_Male  -->
<!-- save(Control_low_dur_Male, file = "../Models/Control_low_dur_Male.Rdata") -->
<!-- Control_low_dur_Male -->
<!-- rpt_low_dur(Anxiety_Treatment_Male) -> Treatment_low_dur_Male  -->
<!-- save(Treatment_low_dur_Male, file = "../Models/Treatment_low_dur_Male.Rdata") -->
<!-- Treatment_low_dur_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_low_dur(Anxiety_Control_Female) -> Control_low_dur_Female  -->
<!-- save(Control_low_dur_Female, file = "../Models/Control_low_dur_Female.Rdata") -->
<!-- Control_low_dur_Female -->
<!-- rpt_low_dur(Anxiety_Treatment_Female) -> Treatment_low_dur_Female -->
<!-- save(Treatment_low_dur_Female, file = "../Models/Treatment_low_dur_Female.Rdata") -->
<!-- Treatment_low_dur_Female -->

<!-- #Repeatability analysis males -->
<!-- rpt_mid_dur(Anxiety_Control_Male) -> Control_mid_dur_Male  -->
<!-- save(Control_mid_dur_Male, file = "../Models/Control_mid_dur_Male.Rdata") -->
<!-- Control_mid_dur_Male -->
<!-- rpt_mid_dur(Anxiety_Treatment_Male) -> Treatment_mid_dur_Male  -->
<!-- save(Treatment_mid_dur_Male, file = "../Models/Treatment_mid_dur_Male.Rdata") -->
<!-- Treatment_mid_dur_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_mid_dur(Anxiety_Control_Female) -> Control_mid_dur_Female  -->
<!-- save(Control_mid_dur_Female, file = "../Models/Control_mid_dur_Female.Rdata") -->
<!-- Control_mid_dur_Female -->
<!-- rpt_mid_dur(Anxiety_Treatment_Female) -> Treatment_mid_dur_Female -->
<!-- save(Treatment_mid_dur_Female, file = "../Models/Treatment_mid_dur_Female.Rdata") -->
<!-- Treatment_mid_dur_Female -->

<!-- #Repeatability analysis males -->
<!-- rpt_high_dur2(Anxiety_Control_Male) -> Control_high_dur_Male  -->
<!-- save(Control_high_dur_Male, file = "../Models/Control_high_dur_Male.Rdata") -->
<!-- Control_high_dur_Male -->
<!-- rpt_high_dur2(Anxiety_Treatment_Male) -> Treatment_high_dur_Male  -->
<!-- save(Treatment_high_dur_Male, file = "../Models/Treatment_high_dur_Male.Rdata") -->
<!-- Treatment_high_dur_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_high_dur(Anxiety_Control_Female) -> Control_high_dur_Female  -->
<!-- save(Control_high_dur_Female, file = "../Models/Control_high_dur_Female.Rdata") -->
<!-- Control_high_dur_Female -->
<!-- rpt_high_dur(Anxiety_Treatment_Female) -> Treatment_high_dur_Female -->
<!-- save(Treatment_high_dur_Female, file = "../Models/Treatment_high_dur_Female.Rdata") -->
<!-- Treatment_high_dur_Female -->

<!-- #Repeatability analysis males -->
<!-- rpt_freezing_dur(Anxiety_Control_Male) -> Control_freezing_dur_Male  -->
<!-- save(Control_freezing_dur_Male, file = "../Models/Control_freezing_dur_Male.Rdata") -->
<!-- Control_freezing_dur_Male -->
<!-- rpt_freezing_dur(Anxiety_Treatment_Male) -> Treatment_freezing_dur_Male  -->
<!-- save(Treatment_freezing_dur_Male, file = "../Models/Treatment_freezing_dur_Male.Rdata") -->
<!-- Treatment_freezing_dur_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_freezing_dur(Anxiety_Control_Female) -> Control_freezing_dur_Female  -->
<!-- save(Control_freezing_dur_Female, file = "../Models/Control_freezing_dur_Female.Rdata") -->
<!-- Control_freezing_dur_Female -->
<!-- rpt_freezing_dur(Anxiety_Treatment_Female) -> Treatment_freezing_dur_Female -->
<!-- save(Treatment_freezing_dur_Female, file = "../Models/Treatment_freezing_dur_Female.Rdata") -->
<!-- Treatment_freezing_dur_Female -->

<!-- #Repeatability analysis males -->
<!-- rpt_latency(Anxiety_Control_Male) -> Control_latency_high_Male  -->
<!-- save(Control_latency_high_Male, file = "../Models/Control_latency_high_Male.Rdata") -->
<!-- Control_latency_high_Male -->
<!-- rpt_latency(Anxiety_Treatment_Male) -> Treatment_latency_high_Male  -->
<!-- save(Treatment_latency_high_Male, file = "../Models/Treatment_latency_high_Male.Rdata") -->
<!-- Treatment_latency_high_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_latency(Anxiety_Control_Female) -> Control_latency_high_Female  -->
<!-- save(Control_latency_high_Female, file = "../Models/Control_latency_high_Female.Rdata") -->
<!-- Control_latency_high_Female -->
<!-- rpt_latency(Anxiety_Treatment_Female) -> Treatment_latency_high_Female -->
<!-- save(Treatment_latency_high_Female, file = "../Models/Treatment_latency_high_Female.Rdata") -->
<!-- Treatment_latency_high_Female -->

<!-- #Repeatability analysis males -->
<!-- rpt_freq(Anxiety_Control_Male) -> Control_freq_high_Male  -->
<!-- save(Control_freq_high_Male, file = "../Models/Control_freq_high_Male.Rdata") -->
<!-- Control_freq_high_Male -->
<!-- rpt_freq(Anxiety_Treatment_Male) -> Treatment_freq_high_Male  -->
<!-- save(Treatment_freq_high_Male, file = "../Models/Treatment_freq_high_Male.Rdata") -->
<!-- Treatment_freq_high_Male -->

<!-- #Repeatability analysis females -->
<!-- rpt_freq(Anxiety_Control_Female) -> Control_freq_high_Female  -->
<!-- save(Control_freq_high_Female, file = "../Models/Control_freq_high_Female.Rdata") -->
<!-- Control_freq_high_Female -->
<!-- rpt_freq(Anxiety_Treatment_Female) -> Treatment_freq_high_Female -->
<!-- save(Treatment_freq_high_Female, file = "../Models/Treatment_freq_high_Female.Rdata") -->
<!-- Treatment_freq_high_Female -->


<!-- ``` -->

