---
title: "Optimism Sex Analysis"
output: html_document
---

### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)

# Load custom functions
source("../Scripts/functions_learning.R")
source("../Scripts/functions_repeatability.R")

```

#Subset data by sex
```{r}
#Subset by sex

#Control and treatment males and females for positive stimulus
Optimism_Control_Male_Positive <- subset(Positive_Control, Positive_Control$Sex == "male")
Optimism_Control_Female_Positive <- subset(Positive_Control, Positive_Control$Sex == "female")
Optimism_Treatment_Male_Positive <- subset(Positive_Treatment, Positive_Treatment$Sex == "male")
Optimism_Treatment_Female_Positive <- subset(Positive_Treatment, Positive_Treatment$Sex == "female")

#Control and treatment males and females for negative stimulus
Optimism_Control_Male_Negative <- subset(Negative_Control, Negative_Control$Sex == "male")
Optimism_Control_Female_Negative <- subset(Negative_Control, Negative_Control$Sex == "female")
Optimism_Treatment_Male_Negative <- subset(Negative_Control, Negative_Control$Sex == "male")
Optimism_Treatment_Female_Negative <- subset(Negative_Control, Negative_Control$Sex == "female")

#Control and treatment males and females for mixed stimulus
Optimism_Control_Male_Mixed <- subset(Mixed_Control, Mixed_Control$Sex == "male")
Optimism_Control_Female_Mixed <- subset(Mixed_Control, Mixed_Control$Sex == "female")
Optimism_Treatment_Male_Mixed <- subset(Mixed_Control, Mixed_Control$Sex == "male")
Optimism_Treatment_Female_Mixed <- subset(Mixed_Control, Mixed_Control$Sex == "female")
```

### MAIN ANALYSIS FOR TIME SPENT NEAR SCREEN (0-5CM)

1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS FOR EACH GROUP AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITIES
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT

# Positive Analysis

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Positive <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Positive_ALL) #mixed model
tab_model(Model_Positive)
hist(residuals(Model_Positive)) #histogram of residuals to check for normal distribution 

Model_Positive0 <- lmer(zone_05_dur ~ Group*Sex + (1 | Fish_ID), data = Positive_ALL) #mixed model, interaction added
tab_model(Model_Positive0)
hist(residuals(Model_Positive0))

#Calculating repeatabilities using custom made functions for males (control and treatment)
rpt_optimism_zone05(Optimism_Control_Male_Positive) -> rpt_positive_control_male
rpt_positive_control_male
rpt_optimism_zone05(Optimism_Treatment_Male_Positive) -> rpt_positive_treatment_male
rpt_positive_treatment_male

#Calculating repeatabilities using custom made functions for females (control and treatment)
rpt_optimism_zone05(Optimism_Control_Female_Positive) -> rpt_positive_control_female
rpt_positive_control_female
rpt_optimism_zone05(Optimism_Treatment_Female_Positive) -> rpt_positive_treatment_female
rpt_positive_treatment_female

#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_zone05(Optimism_Control_Male_Positive) -> within_between_positive_control_male
within_between_positive_control_male
rpt_within_zone05(Optimism_Treatment_Male_Positive) -> within_between_positive_treatment_male
within_between_positive_treatment_male

#Obtaining within-individual and between-individual variance for females (control and treatment)

rpt_within_zone05(Optimism_Control_Female_Positive) -> within_between_positive_control_female
within_between_positive_control_female
rpt_within_zone05(Optimism_Treatment_Female_Positive) -> within_between_positive_treatment_female
within_between_positive_treatment_female

#Obtaining differences between repeatabilities of males and females in the control group
Control_positive_boot_male <- unlist_rptr(rpt_positive_control_male) #unlisting from the males
Control_positive_boot_female <- unlist_rptr(rpt_positive_control_female) #unlisting from the females
positive_diff_control <- difference_boot(Control_positive_boot_male,Control_positive_boot_female) #calculating the difference between males and females in the control group
q_positive_control <- quantiles_diff_boot(positive_diff_control) #obtaining 95% CI
m_positive_control <- mean(positive_diff_control) #Obtaining mean
m_positive_control
q_positive_control

#Obtaining differences between repeatabilities of males and females in the treatment group
Treatment_positive_boot_male <- unlist_rptr(rpt_positive_treatment_male) #unlisting from the males
Treatment_positive_boot_female <- unlist_rptr(rpt_positive_treatment_female) #unlisting from the females
positive_diff_treatment <- difference_boot(Treatment_positive_boot_female,Treatment_positive_boot_male) #calculating the difference between males and females in the control group
q_positive_treatment <- quantiles_diff_boot(positive_diff_treatment) #obtaining 95% CI
m_positive_treatment <- mean(positive_diff_treatment) #Obtaining mean
m_positive_treatment
q_positive_treatment

# Calculating difference in variance between control and treatment groups
Model_Positive1 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, data = Positive_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Positive1)
Model_Positive2 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Positive_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Positive2)
anova(Model_Positive1, Model_Positive2) #calculating difference between two models to find difference in variance

```




# Negative Analysis

```{r}

#Check Normality with mixed model and then histogram of residuals

Model_Negative <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Negative_ALL) #mixed model
tab_model(Model_Negative)
hist(residuals(Model_Negative)) #histogram of residuals to check for normal distribution 

Model_Negative0 <- lmer(zone_05_dur ~ Group*Sex + (1 | Fish_ID), data = Negative_ALL) #mixed model, interaction added
tab_model(Model_Negative0)
hist(residuals(Model_Negative0))

#Calculating repeatabilities using custom made functions for males (control and treatment)
rpt_optimism_zone05(Optimism_Control_Male_Negative) -> rpt_negative_control_male
rpt_negative_control_male
rpt_optimism_zone05(Optimism_Treatment_Male_Negative) -> rpt_negative_treatment_male
rpt_negative_treatment_male

#Calculating repeatabilities using custom made functions for females (control and treatment)
rpt_optimism_zone05(Optimism_Control_Female_Negative) -> rpt_negative_control_female
rpt_negative_control_female
rpt_optimism_zone05(Optimism_Treatment_Female_Negative) -> rpt_negative_treatment_female
rpt_negative_treatment_female

#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_zone05(Optimism_Control_Male_Negative) -> within_between_negative_control_male
within_between_negative_control_male
rpt_within_zone05(Optimism_Treatment_Male_Negative) -> within_between_negative_treatment_male
within_between_negative_treatment_male

#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_zone05(Optimism_Control_Female_Negative) -> within_between_negative_control_female
within_between_negative_control_female
rpt_within_zone05(Optimism_Treatment_Female_Negative) -> within_between_negative_treatment_female
within_between_negative_treatment_female

#Obtaining differences between repeatabilities of males and females in the control group
Control_negative_boot_male <- unlist_rptr(rpt_negative_control_male) #unlisting from the males
Control_negative_boot_female <- unlist_rptr(rpt_negative_control_female) #unlisting from the females
negative_diff_control <- difference_boot(Control_negative_boot_male,Control_negative_boot_female) #calculating the difference between males and females in the control group
q_negative_control <- quantiles_diff_boot(negative_diff_control) #obtaining 95% CI
m_negative_control <- mean(negative_diff_control) #Obtaining mean
m_negative_control
q_negative_control

#Obtaining differences between repeatabilities of males and females in the treatment group
Treatment_negative_boot_male <- unlist_rptr(rpt_negative_treatment_male) #unlisting from the males
Treatment_negative_boot_female <- unlist_rptr(rpt_negative_treatment_female) #unlisting from the females
negative_diff_treatment <- difference_boot(Treatment_negative_boot_female,Treatment_negative_boot_male) #calculating the difference between males and females in the control group
q_negative_treatment <- quantiles_diff_boot(negative_diff_treatment) #obtaining 95% CI
m_negative_treatment <- mean(negative_diff_treatment) #Obtaining mean
m_negative_treatment
q_negative_treatment

# Calculating difference in variance between control and treatment groups
Model_Negative1 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, data = Negative_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Negative1)
Model_Negative2 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Negative_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Negative2)
anova(Model_Negative1, Model_Negative2) #calculating difference between two models to find difference in variance

```

# Mixed Analysis

```{r}

#Check Normality with mixed model and then histogram of residuals

Model_Mixed <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Mixed_ALL) #mixed model
tab_model(Model_Mixed)
hist(residuals(Model_Mixed)) #histogram of residuals to check for normal distribution 

Model_Mixed0 <- lmer(zone_05_dur ~ Group*Sex + (1 | Fish_ID), data = Mixed_ALL) #mixed model, interaction added
tab_model(Model_Mixed0)
hist(residuals(Model_Mixed0))

#Calculating repeatabilities using custom made functions for males (control and treatment)
rpt_optimism_zone05(Optimism_Control_Male_Mixed) -> rpt_mixed_control_male
rpt_mixed_control_male
rpt_optimism_zone05(Optimism_Treatment_Male_Mixed) -> rpt_mixed_treatment_male
rpt_mixed_treatment_male

#Calculating repeatabilities using custom made functions for females (control and treatment)
rpt_optimism_zone05(Optimism_Control_Female_Mixed) -> rpt_mixed_control_female
rpt_mixed_control_female
rpt_optimism_zone05(Optimism_Treatment_Female_Mixed) -> rpt_mixed_treatment_female
rpt_mixed_treatment_female

#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_zone05(Optimism_Control_Male_Mixed) -> within_between_mixed_control_male
within_between_mixed_control_male
rpt_within_zone05(Optimism_Treatment_Male_Mixed) -> within_between_mixed_treatment_male
within_between_mixed_treatment_male

#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_zone05(Optimism_Control_Female_Mixed) -> within_between_mixed_control_female
within_between_mixed_control_female
rpt_within_zone05(Optimism_Treatment_Female_Mixed) -> within_between_mixed_treatment_female
within_between_mixed_treatment_female

#Obtaining differences between repeatabilities of males and females in the control group
Control_mixed_boot_male <- unlist_rptr(rpt_mixed_control_male) #unlisting from the males
Control_mixed_boot_female <- unlist_rptr(rpt_mixed_control_female) #unlisting from the females
mixed_diff_control <- difference_boot(Control_mixed_boot_male,Control_mixed_boot_female) #calculating the difference between males and females in the control group
q_mixed_control <- quantiles_diff_boot(mixed_diff_control) #obtaining 95% CI
m_mixed_control <- mean(mixed_diff_control) #Obtaining mean
m_mixed_control
q_mixed_control

#Obtaining differences between repeatabilities of males and females in the treatment group
Treatment_mixed_boot_male <- unlist_rptr(rpt_mixed_treatment_male) #unlisting from the males
Treatment_mixed_boot_female <- unlist_rptr(rpt_mixed_treatment_female) #unlisting from the females
mixed_diff_treatment <- difference_boot(Treatment_mixed_boot_male,Treatment_mixed_boot_female) #calculating the difference between males and females in the control group
q_mixed_treatment <- quantiles_diff_boot(mixed_diff_treatment) #obtaining 95% CI
m_mixed_treatment <- mean(mixed_diff_treatment) #Obtaining mean
m_mixed_treatment
q_mixed_treatment

# Calculating difference in variance between control and treatment groups
Model_Mixed1 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, data = Mixed_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Mixed1)
Model_Mixed2 <- lme(zone_05_dur ~ Group-1*Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Mixed_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Mixed2)
anova(Model_Mixed1, Model_Mixed2) #calculating difference between two models to find difference in variance
```
