---
title: "Personality"
author: "Hamza"
date: "12/02/2020"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---


### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer, brms, MCMCglmm)

```

### Converting from wide to long data format   
```{r}
Personality <- read.csv("./Data/Personality/ALL.csv")
Post_assay <- read.csv("./Data/Personality/Post-assay.csv")

# making a column with a factor where the four levels correspond to the four phases
Personality$phase <-  factor(Personality$Time, levels = c("6-9", "13-16", "20-23", "27-30")) 

# making a list where each level of the list is a different phase
phases <- split(Personality, Personality$phase)

# function to apply to the four phases: 1, 2, 3, and 4
func_phase <- function(phase = 1){
    df <- phases[[phase]] # getting phase dataframe based on index (1-4)
    df$Behaviour <- df[,paste0("Phase",phase)] # getting columns that says which behaviour was in that phase
    df <- df[,!(names(df) %in% paste0("Phase", 1:4))] # removing the now-redundant Phase1,...,Phase4 columns
    return(df) # return dataframe
}

# applying function, returning a list of four dataframes
Personality_list <- lapply(1:4, function(x) func_phase(x))
Personality_df <- bind_rows(Personality_list) # stakes dataframe on top of each other

# making an ID for the tank info (four phases in a session)
Personality_df <- Personality_df %>% mutate(fish_session_ID = paste(Fish_ID, Date, Session, Camera)) %>% arrange(fish_session_ID) 

# turning from wide to long
vars <- c("tot_dist", "mean_speed", "mean_dist_05",  
          "tot_dist_05", "freeze_dur", "zone_510_dur",  
          "zone_05_dur",  "zone_2025_dur","zone_1520_dur", 
          "zone_3035_dur", "zone_1015_dur", "zone_3540_dur", 
          "zone_2530_dur", "zone_near_dur", "zone_middle_dur", 
          "zone_far_dur",  "arena_dur",  "moving_dur")
info <- c("Time", "Day", "Date",  "Arena",   "Sex", "Mark", "Session", "Camera",  "Group",  "Fish_ID", "Notes")

# four behaviours
behavs <- c("Aggression", "Novel", "Predator", "Social")

# function to rename variables for each behaviour
func_variable_behav <- function(behav = behavs[1]){
    behav_vars <- Personality_df[Personality_df$Behaviour == behav,vars] # getting just the variables for that behaviour
    names(behav_vars) <- paste(names(behav_vars), behav, sep = "_") # renaming variables so they say which behaviour they relate to
    return(behav_vars)
}
# applying function to each behaviour
vars_behavs_list <- lapply(behavs, function(x) func_variable_behav(x))
# putting the four behaviour columns next to each other
vars_behavs <- bind_cols(vars_behavs_list) 

# adding info
Personality_wide <- cbind(Personality_df[Personality_df$Behaviour == "Aggression", info], vars_behavs)


### Adding in activity data (post-assay) to Personality_wide

Personality_wide <- left_join(Post_assay, Personality_wide)

# five behaviours
behavs <- c("Aggression", "Novel", "Predator", "Social", "Activity") #modified to include activity so we can run functions below
```

### Residual distributions and repeatability values for each variable    
Using Shapiro-Wilk normality test   
See ?shapiro.test
More normal = higher W value and smaller p value
```{r}
func_behav_raw <- function(behav = behavs[1]){
  
  func_var <- function(var = vars[1]){
    mod <- lmer(Personality_wide[,paste(var,behav,sep="_")] ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) 
    residuals <- resid(mod)
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)
    sw <- shapiro.test(residuals)
    df <- data.frame(behav, var, rpt, W = round(sw$statistic,3), p = round(sw$p.value,3))
    return(df)
  } # raw general linear model to determine whether transformations are required
  

  
 rpt_vals <- bind_rows(lapply(vars, function(x) func_var(x)))
 return(rpt_vals)
}

func_behav_sqrt <- function(behav = behavs[1]){
  
  func_var <- function(var = vars[1]){
    mod <- lmer(sqrt(Personality_wide[,paste(var,behav,sep="_")]) ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) # added a square root transformation here to the model
    residuals <- resid(mod)
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)
    sw <- shapiro.test(residuals)
    df <- data.frame(behav, var, rpt, W = round(sw$statistic,3), p = round(sw$p.value,3))
    return(df)
  } # same general linear model as above but with a square root transformation
  

  
 rpt_vals <- bind_rows(lapply(vars, function(x) func_var(x)))
 return(rpt_vals)
}

# RUNNING MODELS 

rpt_resids <- bind_rows(lapply(behavs, function(x) func_behav_raw(x))) # not transformed

rpt_resids_sqrt <- bind_rows(lapply(behavs, function(x) func_behav_sqrt(x))) # sqrt transformed

# CHECKING TO SEE WHICH VARIABLES ARE NORMAL AND WHICH REQUIRE TRANSFORMATION

# restricting to just values of W > 0.9 and seeing which variables are represented for all behaviors

rpt_resids %>% filter(W>0.9) %>% group_by(var) %>% tally()


# only mean_speed and tot_dist are there for everything


filter(rpt_resids, var == "mean_speed") # all looks good, except p-val for Aggression?

filter(rpt_resids, var == "tot_dist") # similar to above?

# zone_near_dur there for 4/5, so we want to check which phase would need to be transformed 

filter(rpt_resids, var == "zone_near_dur") 

#this shows that the "Social" phase needs a transformation for the variable zone_near_dur, so we'll see if a square root transformation helps

rpt_resids_sqrt %>% filter(W>0.9) %>% group_by(var) %>% tally()

filter(rpt_resids_sqrt, var == "zone_near_dur")

# The square root transformation doesn't help for the variable zone_near_dur for the Social phase, so will try to identify another variable that can be used for all 5 phases as long as transformations work

rpt_resids %>% filter(W>0.9) %>% group_by(var) %>% tally()

#Will try to see tot_dist_05
 
filter(rpt_resids, var == "tot_dist_05")

#Social and Aggression require transformations, will see if the sqrt transformations helped

filter(rpt_resids_sqrt, var == "tot_dist_05")

#Aggression phase is good with a square root transformation, Social phase improved, possibility it can be used?

# Will now check zone_05_dur

filter(rpt_resids, var == "zone_05_dur")

#Not too fussed with Activity phase as we will use a distance variable, however, Novel phase needs to be transformed. Will see if the transformation helps with normality

filter(rpt_resids_sqrt, var == "zone_05_dur")

#A square root transformation appears to have done the job.

# To summarize, we can use the following variables for analysis

# Mean speed (all 5 phases), total distance (all 5 phases), zone_05_dur (Novel phases requires a square root transformation)
```


### Run lmer models for chosen behaviour   
```{r}
# Chosen variables: total distance for activity, zone_05_dur for stimulus phases

# ROSE: you could modify the function so you can do it all at once:
func_mod_behav_vars  <- function(var,df = Personality_wide){
  mod <- lmer(df[,var] ~ Group*Sex + (1 | Fish_ID), data = df)
  if(str_detect(var, "Novel")){ # if the variable = Novel, we will square-root the variable
    mod <- lmer(sqrt(df[,var]) ~ Group*Sex + (1 | Fish_ID), data = df) 
  }

  return(mod) 
  
}

behav_vars <- c("zone_05_dur_Social", "zone_05_dur_Predator", "zone_05_dur_Novel", "zone_05_dur_Aggression", "tot_dist_Activity") # including novel and changing activity from zone_05_dur to tot_dist_Activity
mod_list_5behav <- lapply(behav_vars, function(x) func_mod_behav_vars(x)) 
names(mod_list_5behav) <- behav_vars

lmer_zone_05_dur_Social <- lmer(zone_05_dur_Social ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) #Extra model to check

fixef(lmer_zone_05_dur_Social) == fixef(mod_list_5behav$zone_05_dur_Social) # they're the same

#lmer_zone_05_dur_Novel <- lmer(sqrt(zone_05_dur_Novel) ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) # Extra model to check

```


### Extract BLUPs from lmer models and plot fitted versus. predicted      
- make a dataframe with the model parameters    
- fitted = the actual measured behaviors
- predicted = the model predictions, calculated according to the below equation:

$$y_{ij} = \beta_0 + \text{ID}_j + \beta_1(\text{treatment})+ \beta_2(\text{male}) + \beta_3(\text{treatment}\cdot\text{male}) + e_i$$ 
$$\text{ID} \sim \text{N}(0,\sigma^2_{\text{ID}})$$
$$e \sim \text{N}(0,\sigma^2_{\text{e}})$$

```{r}

func_fitted_predicted_lmer <- function(variable = behav_vars[1]){ 
  mod <- mod_list_5behav[[variable]] # using the variable name to get the model
  #getting population parameters
  betas <- fixef(mod)
b0 <- betas[1]
b1 <- betas[2]
b2 <- betas[3]
b3 <- betas[4]
# getting blups
blups <- data.frame(ranef(mod))
round(mean(blups$condval)) # average of blups = 0
# finding the treatment and male value for each fish_ID
fish_ID <- as.character(blups$grp)
# need to match fish_ID ID with their info
pos <- match(fish_ID, Personality_wide$Fish_ID)
mod_pars <- data.frame(fish_ID, b0, ID = blups$condval, b1, b2, b3, treatment = ifelse(Personality_wide$Group[pos] == "Treatment",1,0), male = ifelse(Personality_wide$Sex[pos]=="male",1,0)) %>% mutate(predicted = b0 + ID + b1*treatment + b2*male + b3*(treatment*male))
(Personality_wide$Fish_ID[pos] == fish_ID) # all TRUE
# finding predicted values
pos <- match(Personality_wide$Fish_ID, mod_pars$fish_ID)
(mod_pars$fish_ID[pos]==Personality_wide$Fish_ID) # all TRUE
fitted_predicted <- mod_pars[pos,] 
fitted_predicted$fitted<- Personality_wide[,variable]

# my_index <- which(fitted_predicted$variable_name == "zone_05_dur_Novel" & fitted_predicted$predicted)
# 
# fitted_predicted$predicted[my_index] <- sqrt(fitted_predicted$predicted[my_index])

#HAMZA: From my understanding, the predicted values need to be square rooted, so I have added the above, but I don't think it is working when the function is run, it seems to work when running on its own, Ihave hashed it out for now as it doesn't seem to be working correctly, see below

fitted_predicted$variable_name <- variable
return(fitted_predicted) 
}

# applying this function to our variables
fitted_predicted_lmer_list <- lapply(behav_vars, function(x) func_fitted_predicted(variable = x))
names(fitted_predicted_lmer_list) <- behav_vars

fitted_predicted_lmer_list$zone_05_dur_Novel$predicted <- sqrt(fitted_predicted_lmer_list$zone_05_dur_Novel$predicted) #HAMZA: Or I can do this after we have run lapply? Is an extra step which is not ideal 

# Function to plot fitted vs. predicted and calculate R2
func_fitted_predicted_plots <- function(df =
                                          fitted_predicted_list[[2]]){
  behav<- gsub(".*dur\\_|.*dist\\_", "", df$variable_name[1]) 
  
  R2<- cor(df$fitted, df$predicted)^2 %>% round(3)
  
  plot<- ggplot(df)+
    theme_classic()+
    geom_point(aes(x=fitted, y=predicted))+
    labs(x=df$variable_name[1],
         title=behav,subtitle=paste0("R2 = ", R2))
  
  return(plot)
}

plot_list_behavs <- lapply(fitted_predicted_lmer_list, function(x) func_fitted_predicted_plots(x))

plot_list_behavs[[1]]
plot_list_behavs[[2]]
plot_list_behavs[[3]]
plot_list_behavs[[4]]
plot_list_behavs[[5]]

```


### Repeat the above steps in brm (which uses stan), and compare the results to the lmer models   
```{r}
#Here To-do:

# - Write a function that will input your brm model object, and output two things: (1) the posterior distributions of population paramaters; (2) the fitted and predicted values for posterior means.
behav_vars <- c("zone_05_dur_Social", "zone_05_dur_Predator", "zone_05_dur_Novel", "zone_05_dur_Aggression", "tot_dist_Activity") 


load("./Models/mod_list_brms.Rdata")

options(mc.scores = parallel::detectCores())


func_brm_mod <- function(var, df = Personality_wide){
  df$response <- df[,var] # formula argument relies entirely on the data argument, so you can't just call the columns directly

  if(str_detect(var, "Novel")){ 
    brm <- brm(formula = sqrt(response) ~ Group*Sex + (1 | Fish_ID), 
                                  data = df,
                                  family = gaussian(),
                                  chains = 3,
                                 iter = 2000, warmup = 1000)
  }else{ # ROSE TIP: before, for novel, you had to run two models. Now, you only run one (one of the other). Because baysian models take a while to run, this will speed up the function.
      brm <- brm(formula = response ~ Group*Sex + (1 | Fish_ID), 
                                  data = df,
                                  family = gaussian(),
                                  chains = 3,
                                 iter = 2000, warmup = 1000)
  }

  return(brm)
}


# mod_list_brms <- lapply(behav_vars, function(x) func_brm_mod(x))
# names(mod_list_brms) <- behav_vars
# save(mod_list_brms, file = "./Models/mod_list_brms.Rdata")

# Rose's tips:

func_process_mod_brm <- function(variable = behav_vars[1]){
    mod <- mod_list_brms[[variable]]
    
  mod_posterior <- as.data.frame(mod)
  pop_posterior <- select(mod_posterior,!contains(c("r_Fish_ID", "lp"))) #We don't want to get rid of the variance component ! Hence why "r_Fish_ID" and not "Fish_ID"
  
  b0 <- pop_posterior[,"b_Intercept"] 
  b1 <- pop_posterior[, "b_GroupTreatment"]
  b2 <- pop_posterior[, "b_Sexmale"]
 # b3 <- pop_posterior[, "b_GroupTreatment.Sexmale"] # ROSE: this is an error
  b3 <- pop_posterior[, "b_GroupTreatment.Sexmale"] #I had to change it back as there's no ":", only a "."
  sigma_e <- pop_posterior[, "sigma"]
  #var_comp <- pop_posterior[, "sd_Fish_ID__Intercept"] # not quite the right name
  sigma_ID <- pop_posterior[, "sd_Fish_ID__Intercept"]

  #HAMZA: These do not seem to be renamed once we run lapply, is this because below we have overrided ? We are naming the co-efficients fromt the means as the same things, does this matter?
  
  # next, get the posterior means, as you did above
   post_means <- apply(mod_posterior, 2, function(x) mean(x)) # except we don't round because we're using these in subsequent calculations
  
  # to make fitted_predicted, the logic is as follows:
   
   # we have:
   fitted <- Personality_wide[,c("Fish_ID", "Sex", "Group", variable)]
   names(fitted)[names(fitted)==variable] <- "fitted" #THIS STEP IMPORTANT !
   # TO-DO: remember to update this to novel so it's square-root
   
  #HAMZA: The predicted values ? See below as I have done a little thing following lapply
   
   # and we need to get what the model predicted. So you need to solve the model equation from line 219, predicted = B0 + individual_difference + B1*treatment + B2*male + B3*treatment*male.
   
   # to do this calculation, make three more columns from 'fitted': a column of 1s and 0s for treatment,a column of 1s and 0s for male, and a column of individual_difference, which you will get by matching the Fish_ID in each row to the mean BLUP from post_means

   # ROSE:
   blups <- post_means[str_detect(names(post_means), "r_Fish_ID")] # here are your individual differences
   # now use gsub to rename them so the name is just the fish_ID
   names(blups) # see how these are all in the format r_Fish_ID[aXXXX,Intercept]? You need to get them to all be aXXXX, then you can match them up with the fish_IDs in the fitted dataframe.
   
names(blups) <- gsub(".*Fish_ID.", "",  names(blups))
names(blups) <- gsub(".Intercept.", "", names(blups))
# I did this in two steps because I'm not sure how to keep the middle of the string without ruining the entire thing :/ 
names(blups) # Double checking to make sure we have renamed correctly

 fish_ID <- as.character(names(blups)) #converting to characters as we did above, is this completely necessary ? Code seems to work regardless of it
  
  
  # ROSE tip: when you get stuck doing something complicated, it's always best to break it down into little steps (rather than the one line below)
  
  # step one: get the order of fish in the fitted dataset
  fitted_fish <- fitted$Fish_ID
  
  # step two: get an indexing vector to put the indiv differences in the same order as fish in the fitted dataset
  pos <- match(fitted_fish, fish_ID) # for match, the first argument is the reference, and the second argument is the one you are retrieving an index for 
  
  # always check that the matching is correct
  fish_ID[pos] == fitted_fish # all TRUE
  # you can also check like this:
  sum(fish_ID[pos] == fitted_fish) == length(fitted_fish)
  
  # step three: get a vector of the individual differences
  ID <- blups[pos]
  # checking this is right
  names(ID) == fitted_fish
  
  # step four: get columns for the categorical variables of 'male', 'treatment', and 'treatment*male'
  male <- ifelse(fitted$Sex=="male",1,0) #Has to be lower case
  treatment <- ifelse(fitted$Group=="Treatment",1,0)
  treatment.male <- ifelse(fitted$Group=="Treatment"&fitted$Sex=="male",1,0) #Changed to lower case
  
  # step five: get the posterior mean estimates for your model coefficients: intercept male contrast treatment contrast and male + treatment interaction
  b0 <- post_means["b_Intercept"] 
  b1 <- post_means["b_GroupTreatment"]
  b2 <- post_means["b_Sexmale"]
  b3 <- post_means["b_GroupTreatment.Sexmale"] #Only works with "."
  
  # step six: do the maths to get your predicted values
  predicted <- b0 + ID + b1*treatment + b2*male + b3*treatment.male
  
  # step seven: make your dataframe for export
  fitted_predicted <- data.frame(fish_ID = fitted_fish, 
                                 fitted = fitted$fitted,
                                 b0, ID, b1, b2, b3,
                                 treatment, male, 
                                 predicted, 
                                 variable_name = variable
                                 )

   
  return(list(pop_posterior, fitted_predicted))
  
}


# Next: apply func_process_mod() to all your variables 
fitted_process_brm_list <- lapply(behav_vars, function(x) func_process_mod_brm(variable = x))
names(fitted_process_brm_list) <- behav_vars

fitted_process_brm_list$zone_05_dur_Novel[[2]]$predicted <- sqrt(fitted_process_brm_list$zone_05_dur_Novel[[2]]$predicted)

# note that each item in the list is, itself, a list. If you want to get the first element of each list (pop_posterior), you can go lapply(fitted_process_brm_list, function(x) x[[1]])

# TASK ONE: plot fitted vs. predicted for lmer and brm models on the same plot (using different colours for the different models)
# you can use the functon func_fitted_predicted_plots() from the previous section as a guide


#HAMZA: So we want one plot of both models fitted and predicted, overlapping? Or one plot with separate panels?

# Function to plot fitted vs. predicted and calculate R2
func_fit_pred_plots_brms <- function(df1 = fitted_process_brm_list[[2]]){
  
  behav<- gsub(".*dur\\_|.*dist\\_", "", df1[[2]]$variable_name[1]) 
  
  R2<- cor(df1[[2]]$fitted, df1[[2]]$predicted)^2 %>% round(3)
  
  plot<- ggplot(df1[[2]])+
    theme_classic()+
    geom_point(aes(x=fitted, y=predicted, color='#A4A4A4'))+ #
    theme(legend.position = "none")+
    labs(x=df1[[2]]$variable_name[1],
         title=behav,subtitle=paste0("R2 = ", R2))
  
  return(plot)
}

plot_list_behavs_brms <- lapply(fitted_process_brm_list, function(x) func_fit_pred_plots_brms(x))

plot_list_behavs_brms[[1]]
plot_list_behavs_brms[[2]]
plot_list_behavs_brms[[3]]
plot_list_behavs_brms[[4]]
plot_list_behavs_brms[[5]]

#Attempting to join the two plots together
plot <- ggplot()+
    theme_classic()+
    geom_point(data = df1[[2]], aes(x=fitted, y=predicted, color='#A4A4A4'))+
    theme(legend.position = "none")+
  
geom_point(data=df, aes(x=fitted, y=predicted))

#Rough example I guess but not really sure if I am doing it correctly, or if I have done the brms models correctly either

# TASK TWO: calculate repeatability for all behaviours from the brm models. 

#HAMZA: Need to use variance component that would be in the pop_posterior dataset

#Would need to utilize these but in a function
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)

 func_var_rpt_brms <- function(variable = behav_vars[1]){
    mod <- mod_list_brms[[variable]]
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)
   df2 <- data.frame(behav_vars, variable, rpt)
    return(df2)
 }
 
 fitted_process_brm_list_rpt <- lapply(func_var_rpt_brms, function(x) func_var_rpt_brms(variable = x))
names(fitted_process_brm_list_rpt) <- behav_vars

```





