---
title: "Personality"
author: "Hamza"
date: "12/02/2020"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---


### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer, brms, MCMCglmm)

```



### ROSE: converting from wide to long data format   
```{r}
Personality <- read.csv("./Data/Personality/ALL.csv")
Post_assay <- read.csv("./Data/Personality/Post-assay.csv")

# making a column with a factor where the four levels correspond to the four phases
Personality$phase <-  factor(Personality$Time, levels = c("6-9", "13-16", "20-23", "27-30")) 

# making a list where each level of the list is a different phase
phases <- split(Personality, Personality$phase)

# function to apply to the four phases: 1, 2, 3, and 4
func_phase <- function(phase = 1){
    df <- phases[[phase]] # getting phase dataframe based on index (1-4)
    df$Behaviour <- df[,paste0("Phase",phase)] # getting columns that says which behaviour was in that phase
    df <- df[,!(names(df) %in% paste0("Phase", 1:4))] # removing the now-redundant Phase1,...,Phase4 columns
    return(df) # return dataframe
}

# applying function, returning a list of four dataframes
Personality_list <- lapply(1:4, function(x) func_phase(x))
Personality_df <- bind_rows(Personality_list) # stakes dataframe on top of each other

# making an ID for the tank info (four phases in a session)
Personality_df <- Personality_df %>% mutate(fish_session_ID = paste(Fish_ID, Date, Session, Camera, Tank)) %>% arrange(fish_session_ID) # ROSE2: since the 'ALL.csv' data file has been updated, 'Tank' column is missing, so this needs to change
Personality_df <- Personality_df %>% mutate(fish_session_ID = paste(Fish_ID, Date, Session, Camera)) %>% arrange(fish_session_ID) # ROSE2: correction since data update

# turning from wide to long
vars <- c("tot_dist", "mean_speed", "mean_dist_05",  
          "tot_dist_05", "freeze_dur", "zone_510_dur",  
          "zone_05_dur",  "zone_2025_dur","zone_1520_dur", 
          "zone_3035_dur", "zone_1015_dur", "zone_3540_dur", 
          "zone_2530_dur", "zone_near_dur", "zone_middle_dur", 
          "zone_far_dur",  "arena_dur",  "moving_dur")
info <- c("Time", "Day", "Date", "Video",   "Arena",   "Sex", "Mark", "Session", "Camera",  "Tank", "Group",  "Fish_ID", "Notes") # ROSE2: again, not working after data update
info[!(info %in% names(Personality_df))] # Tank and Video missing
info <- c("Time", "Day", "Date",  "Arena",   "Sex", "Mark", "Session", "Camera",  "Group",  "Fish_ID", "Notes")#ROSE2: removing missing tank and video

# four behaviours
behavs <- c("Aggression", "Novel", "Predator", "Social")

# function to rename variables for each behaviour
func_variable_behav <- function(behav = behavs[1]){
    behav_vars <- Personality_df[Personality_df$Behaviour == behav,vars] # getting just the variables for that behaviour
    names(behav_vars) <- paste(names(behav_vars), behav, sep = "_") # renaming variables so they say which behaviour they relate to
    return(behav_vars)
}
# applying function to each behaviour
vars_behavs_list <- lapply(behavs, function(x) func_variable_behav(x))
# putting the four behaviour columns next to each other
vars_behavs <- bind_cols(vars_behavs_list) 

# adding info
Personality_wide <- cbind(Personality_df[Personality_df$Behaviour == "Aggression", info], vars_behavs)
```

### Adding in activity data (post-assay) to Personality_wide
```{r}
Personality_wide <- left_join(Post_assay, Personality_wide)
# 
# # Was a simple task considering the post-assay period was just one set period in all videos. Left join was all that was required to join by the same variables. The joining was successful considering that the number of observations did not change, however the number of variables increased. Cleaning up the original excel file also meant joining was easy. 
# 
# names(Personality_wide)[names(Personality_wide)=="Phase"] <- "Phase5"
# # dplyr wasn't working so had to use base functions for now to just incorporate activity as "Phase5"# ROSE2: not sure what is meant by this?

# five behaviours
behavs <- c("Aggression", "Novel", "Predator", "Social", "Activity") #modified to include activity so we can run functions below

#Data was double checked by Rose
```


### ROSE: residual distributions and repeatability values for each variable    
Using Shapiro-Wilk normality test   
See ?shapiro.test
More normal = higher W value and smaller p value
```{r}
func_behav_raw <- function(behav = behavs[1]){
  
  func_var <- function(var = vars[1]){
    mod <- lmer(Personality_wide[,paste(var,behav,sep="_")] ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) 
    residuals <- resid(mod)
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)
    sw <- shapiro.test(residuals)
    df <- data.frame(behav, var, rpt, W = round(sw$statistic,3), p = round(sw$p.value,3))
    return(df)
  } # raw general linear model to determine whether transformations are required
  

  
 rpt_vals <- bind_rows(lapply(vars, function(x) func_var(x)))
 return(rpt_vals)
}

func_behav_sqrt <- function(behav = behavs[1]){
  
  func_var <- function(var = vars[1]){
    mod <- lmer(sqrt(Personality_wide[,paste(var,behav,sep="_")]) ~ Group*Sex + (1 | Fish_ID), data = Personality_wide) # added a square root transformation here to the model
    residuals <- resid(mod)
    VC <- data.frame(VarCorr(mod))
    rpt <- round(VC$vcov[1]/sum(VC$vcov),2)
    sw <- shapiro.test(residuals)
    df <- data.frame(behav, var, rpt, W = round(sw$statistic,3), p = round(sw$p.value,3))
    return(df)
  } # same general linear model as above but with a square root transformation
  

  
 rpt_vals <- bind_rows(lapply(vars, function(x) func_var(x)))
 return(rpt_vals)
}

# RUNNING MODELS 

rpt_resids <- bind_rows(lapply(behavs, function(x) func_behav_raw(x))) # not transformed

rpt_resids_sqrt <- bind_rows(lapply(behavs, function(x) func_behav_sqrt(x))) # sqrt transformed

# CHECKING TO SEE WHICH VARIABLES ARE NORMAL AND WHICH REQUIRE TRANSFORMATION

# restricting to just values of W > 0.9 and seeing which variables are represented for all behaviors

rpt_resids %>% filter(W>0.9) %>% group_by(var) %>% tally()


# only mean_speed and tot_dist are there for everything


filter(rpt_resids, var == "mean_speed") # all looks good, except p-val for Aggression?

filter(rpt_resids, var == "tot_dist") # similar to above?

# zone_near_dur there for 4/5, so we want to check which phase would need to be transformed 

filter(rpt_resids, var == "zone_near_dur") 

#this shows that the "Social" phase needs a transformation for the variable zone_near_dur, so we'll see if a square root transformation helps

rpt_resids_sqrt %>% filter(W>0.9) %>% group_by(var) %>% tally()

filter(rpt_resids_sqrt, var == "zone_near_dur")

# The square root transformation doesn't help for the variable zone_near_dur for the Social phase, so will try to identify another variable that can be used for all 5 phases as long as transformations work

rpt_resids %>% filter(W>0.9) %>% group_by(var) %>% tally()

#Will try to see tot_dist_05
 
filter(rpt_resids, var == "tot_dist_05")

#Social and Aggression require transformations, will see if the sqrt transformations helped

filter(rpt_resids_sqrt, var == "tot_dist_05")

#Aggression phase is good with a square root transformation, Social phase improved, possibility it can be used?

# Will now check zone_05_dur

filter(rpt_resids, var == "zone_05_dur")

#Not too fussed with Activity phase as we will use a distance variable, however, Novel phase needs to be transformed. Will see if the transformation helps with normality

filter(rpt_resids_sqrt, var == "zone_05_dur")

#A square root transformation appears to have done the job.

# To summarize, we can use the following variables for analysis

# Mean speed (all 5 phases), total distance (all 5 phases), zone_05_dur (Novel phases requires a square root transformation)





```


### Run lmer models for chosen behaviour   
```{r}
#ROSE2: To-do:
# - Write a function that will input your variable name and output the model
# - use lapply to apply that function across all behaviors
# - add more notes/annotation justifying your chosen variables

#Variables of choice due to normality analysis

# Mean speed (all 5 phases), total distance (all 5 phases), zone_05_dur (Novel phases requires a square root transformation)

#Variables are also biologically relevant, in particular time spent near the stimulus screen (zone_05_dur)

# First we require our function for mixed models
func_mod <- function(var,squareroot = F, df = Personality_wide){
  mod <- lmer(df[,var] ~ Group*Sex + (1 | Fish_ID), data = df)
  if(squareroot == TRUE){
    mod <- lmer(sqrt(df[,var]) ~ Group*Sex + (1 | Fish_ID), data = df) #Note how we added a square root transformation if needed
  }

  return(mod) #Must return the model and not the summary of the model
  
}

# testing the function
func_mod("tot_dist_Novel")

#Total distance

tot_dist <- c("tot_dist_Novel", "tot_dist_Social", "tot_dist_Predator", "tot_dist_Activity", "tot_dist_Aggression") #creating a vector to use when we apply models to all behaviors

mod_list <- lapply(tot_dist, function(x) func_mod(x)) #using lapply to apply function to all behaviors

names(mod_list) <- tot_dist # Assigning names to the models, am not sure if I could've done this earlier but will ensure I named the elements of the list correctly

tot_dist_Novel_check <- lmer(tot_dist_Novel ~ Group*Sex + (1 | Fish_ID), data = Personality_wide)
tab_model(tot_dist_Novel_check) #See tab that appears on right side and now compare to your lapply version

mod_list$tot_dist_Novel #Summaries match

tot_dist_Social_check <- lmer(tot_dist_Social ~ Group*Sex + (1 | Fish_ID), data = Personality_wide)
tab_model(tot_dist_Social_check) #See tab that appears on right side and now compare to the lapply version

mod_list$tot_dist_Social #Summaries match

hist(residuals(tot_dist_Social_check)) #Checking to see if residuals match

hist(residuals(mod_list$tot_dist_Social)) #Residuals matching

#From these summaries, am confident the rest of the model summaries are matching as it is following the order of the vector

#Mean speed

mean_speed <- c("mean_speed_Novel", "mean_speed_Social", "mean_speed_Predator", "mean_speed_Activity", "mean_speed_Aggression") #creating a vector to use when we apply models to all behaviors

mod_list_speed <- lapply(mean_speed, function(x) func_mod(x))

names(mod_list_speed) <- mean_speed

mod_list_speed

#Zone 05 duration (time spent near stimulus screen)

zone_05 <- c("zone_05_dur_Social", "zone_05_dur_Predator", "zone_05_dur_Activity", "zone_05_dur_Aggression") #not including novel behavior as this requires a transformation, however we can go ahead and use lapply to apply our function to the other 4 behaviors

mod_list_zone05 <- lapply(zone_05, function(x) func_mod(x)) 

names(mod_list_zone05) <- zone_05



#Don't need lapply for one behavior, so can go ahead and use the function

lmer_zone_05_dur_Novel <- func_mod("zone_05_dur_Novel", squareroot = TRUE)
hist(residuals(lmer_zone_05_dur_Novel)) #Residuals appear better



```


### Extract BLUPs from lmer models and plot fitted versus. predicted      
- make a dataframe with the model parameters    
- fitted = the actual measured behaviors
- predicted = the model predictions, calculated according to the below equation:

$$y_{ij} = \beta_0 + \text{ID}_j + \beta_1(\text{treatment})+ \beta_2(\text{male}) + \beta_3(\text{treatment}\cdot\text{male})$$ 


```{r}
#ROSE2: To-do:
# - Write a function that will input your model name and output your dataframe of fitted and predicted values   
# - use lapply to apply that function across all your models  

#HAMZA2: Having trouble with the lapply because I can't figure out how to use gsub properly :/

# example:
mod = tot_dist_Novel_check #For the gsubbing, we just need any example

mod_name = "tot_dist_Novel_check"
mod = get(mod_name)

gsub("lmer\\_", "", mod_name) -> var_name


# getting population parameters
betas <- fixef(mod)
b0 <- betas[1]
b1 <- betas[2]
b2 <- betas[3]
b3 <- betas[4]

# getting blups
blups <- data.frame(ranef(mod))
round(mean(blups$condval)) # average of blups = 0

# finding the treatment and male value for each fish_ID
fish_ID <- as.character(blups$grp)
# need to match fish_ID ID with their info
pos <- match(fish_ID, Personality_wide$Fish_ID)
(Personality_wide$Fish_ID[pos] == fish_ID) # all TRUE

# making dataframe of parameters
mod_pars <- data.frame(fish_ID, b0, ID = blups$condval, b1, b2, b3, treatment = ifelse(Personality_wide$Group[pos] == "Treatment",1,0), male = ifelse(Personality_wide$Sex[pos]=="male",1,0)) %>% mutate(predicted = b0 + ID + b1*treatment + b2*male + b3*(treatment*male))
# finding predicted values
pos <- match(Personality_wide$Fish_ID, mod_pars$fish_ID)
(mod_pars$fish_ID[pos]==Personality_wide$Fish_ID) # all TRUE
fitted_predicted <- mod_pars[pos,] %>% mutate(fitted = Personality_wide$tot_dist_Novel)
plot(fitted_predicted$fitted, fitted_predicted$predicted)
cor(fitted_predicted$fitted, fitted_predicted$predicted)^2 # R2 value


func_fitted_predicted <- function(mod,variable){ #I have so far just put the top code into the function :/
  betas <- fixef(mod)
  b0 <- betas[1]
b1 <- betas[2]
b2 <- betas[3]
b3 <- betas[4]
# getting blups
blups <- data.frame(ranef(mod))
round(mean(blups$condval)) # average of blups = 0
# finding the treatment and male value for each fish_ID
fish_ID <- as.character(blups$grp)
# need to match fish_ID ID with their info
pos <- match(fish_ID, Personality_wide$Fish_ID)
(Personality_wide$Fish_ID[pos] == fish_ID) # all TRUE
# finding predicted values
pos <- match(Personality_wide$Fish_ID, mod_pars$fish_ID)
(mod_pars$fish_ID[pos]==Personality_wide$Fish_ID) # all TRUE
fitted_predicted <- mod_pars[pos,] %>% mutate(fitted = variable)#This is where I'm having trouble, because it has to be unique and I'm not sure how to use gsub here :/
lt = list=c(plot(fitted_predicted$fitted, fitted_predicted$predicted),cor(fitted_predicted$fitted, fitted_predicted$predicted)^2)
return(lt) #return both the R2 value as well as the plot of fitted vs residuals

}

func_fitted_predicted(mod_list$tot_dist_Novel, Personality_wide$tot_dist_Novel) 

#function appears to be working as I am using a different variable and I'm getting an R2 value as well as the plot of fitted vs residuals,however this won't work with lapply because I'm relying on inputting the specific model and specific variable from the datasheet :/ Need to use gsub or vars_behavs but can't quite figure it out :(

mod_list_all <- c(mod_list, mod_list_speed, mod_list_zone05, lmer_zone_05_dur_Novel) #Am sure this is the way to create the list to use in lapply

fit_predict_list <- lapply(mod_list_all, function(x) func_fitted_predicted(x)) #How I would use lapply once I figure out my issue
```


### Repeat the above steps in brm (which uses stan), and compare the results to the lmer models   
```{r}
#ROSE2: To-do:
# - Write a function that will input your variable name, run, and save your brm model 
# - use lapply to apply that function across all your variable names
# - save one Rdata file with all your brm models   
# - Write a function that will input your brm model object, and output two things: (1) the posterior distributions of population paramaters; (2) the fitted and predicted values for posterior means.


library(brms)
load("./Models/mod_list_brms.Rdata")
load("./Models/mod_list_speed_brms.Rdata")
load("./Models/mod_list_speed_brms.Rdata")
load("./Models/zone_05_dur_Novel_brms.Rdata")

options(mc.scores = parallel::detectCores())


func_brm_mod <- function(var, squareroot = F, df = Personality_wide){
  df$response <- df[,var] # formula argument relies entirely on the data argument, so you can't just call the columns directly
  brm <- brm(formula = response ~ Group*Sex + (1 | Fish_ID), 
                                  data = df,
                                  family = gaussian(),
                                  chains = 3,
                                 iter = 2000, warmup = 1000)
  if(squareroot == TRUE){
    brm <- brm(formula = sqrt(response) ~ Group*Sex + (1 | Fish_ID), 
                                  data = df,
                                  family = gaussian(),
                                  chains = 3,
                                 iter = 2000, warmup = 1000)
  }

  return(brm)
}

#Testing function
func_brm_mod("tot_dist_Novel") #Function works !

#Using lapply to use function for all behaviors for total distance, mean speed and zone_05_dur

# total distance
mod_list_brms <- lapply(tot_dist, function(x) func_brm_mod(x))
names(mod_list_brms) <- tot_dist
save(mod_list_brms, file = "./Models/mod_list_brms.Rdata")

# mean speed
mod_list_speed_brms <- lapply(mean_speed, function(x) func_brm_mod(x))
names(mod_list_speed_brms) <- mean_speed
save(mod_list_speed_brms, file = "./Models/mod_list_speed_brms.Rdata")

# zone_05_dur
mod_list_zone05_brms <- lapply(zone_05, function(x) func_brm_mod(x)) 
names(mod_list_zone05_brms) <- zone_05
save(mod_list_zone05_brms, file = "./Models/mod_list_zone05_brms.Rdata")

zone_05_dur_Novel_brms <- func_brm_mod("zone_05_dur_Novel", squareroot = TRUE)
# as this required a square root transformation
save(zone_05_dur_Novel_brms, file = "./Models/zone_05_dur_Novel_brms.Rdata")


#Function for (1) the posterior distributions of population parameters; (2) the fitted and predicted values for posterior means.

func_brm_fit_post <- function(mod){
  mod_posterior <- as.data.frame(mod)
  post_means <- apply(mod_posterior, 2, function(x) round(mean(x),4))
  lt <- list(mod_posterior, post_means)
  return(lt)
}

#Again, am having trouble regarding how I use lapply and applying the function to all the elements in the list and returning them separately

func_brm_fit_post(zone_05_dur_Novel_brms)
```





