---
title: "CORRELATION ANALYSIS"
author: "Hamza"
date: "28/01/2021"
output: html_document
---

### Load packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#loads packages
library(brms)
library(stringr)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(readxl)
```

STEPS
1. Join dataframes to make a new wide data frame of anxiety and personality (matched depending on weeks of measurement)
2. Exploratory analysis with mixed models to decide which behaviors are repeatable and can be used in analysis
3. Correlation analysis using brms and stan

### Import Data - Anxiety
```{r, include=FALSE}
Anxiety_Joined <- read_xlsx("../Data/Anxiety/Anxiety_Data_cor.xlsx")

str(Anxiety_Joined)

#Convert characters into factors

Anxiety_Joined$Sex <- as.factor(Anxiety_Joined$Sex)
Anxiety_Joined$Group <- as.factor(Anxiety_Joined$Group)
Anxiety_Joined$Fish_ID <- as.factor(Anxiety_Joined$Fish_ID)
Anxiety_Joined$Day_Anxiety <- as.factor(Anxiety_Joined$Day_Anxiety)
Anxiety_Joined$Tank <- as.factor(Anxiety_Joined$Tank)
Anxiety_Joined$M.ID <- as.factor(Anxiety_Joined$M.ID)

```

#Joining personality and anxiety data frame
```{r}
#Load "Personality_wide" from previous code
#Filtering to mutate new columns to add "M.ID" for personality dataset

df <- Personality_wide %>% filter(Date == "29/07/2019") %>% mutate(M.ID = "1")
df2 <- Personality_wide %>% filter(Date == "30/07/2019") %>% mutate(M.ID = "1")
df3 <- Personality_wide %>% filter(Date == "20/08/2019") %>% mutate(M.ID = "2")
df4 <- Personality_wide %>% filter(Date == "21/08/2019") %>% mutate(M.ID = "2")
df5 <- Personality_wide %>% filter(Date == "12/09/2019") %>% mutate(M.ID = "3")
df6 <- Personality_wide %>% filter(Date == "13/09/2019") %>% mutate(M.ID = "3")

Personality_wide_new <- bind_rows(df, df2, df3, df4, df5, df6)

dplyr::rename(Personality_wide_new, Day_Personality = Day, Date_Personality = Date)

#Joining anxiety and personality data frames

anxiety_personality_wide <- left_join(Anxiety_Joined, Personality_wide_new, by = c("Fish_ID", "Group", "M.ID", "Sex", "Mark"))

str(anxiety_personality_wide)

# Change all character columns into factors
anxiety_personality_wide %>% type.convert() -> anxiety_personality_wide 

anxiety_personality_wide <- as.data.frame(anxiety_personality_wide) #convert to data frame

```




#Function for running bivar models (both control and treatment combined)
```{r}
# We will only be using one anxiety variable, that is time spent in the low zone (repeatbable and most relevant in zebrafish anxiety literature)


#Function for other models
#NOTE: Need to increase chains and iterations once prelim analysis complete

bivar_model <- function(var1,var2, df = anxiety_personality_wide){
  df$response1 <- df[,var1]
  df$response2 <- df[,var2]
formula1 <- bf(response1 ~ Group*Sex  + (1 | 2 |Fish_ID))
formula2 <- bf(response2 ~ Group*Sex  + (1 | 2 |Fish_ID))
bivar_formula <- mvbrmsformula(formula1, formula2)
bivar <- brm(formula = bivar_formula,
                     data = df,
                     family = gaussian(),
                     chains = 1,
                     iter = 6000, warmup = 2000)
return(bivar)
}

#Combinations required for bivar models
# low dur vs. zone_05_dur_aggression
# low dur vs. zone_05_dur_predator 
# low_dur vs. zone_05_dur_social
# low_dur vs. zone_05_dur_novel
# low_dur vs. tot_dist_activity

#run and save bivar models
anxiety_predator <- bivar_model("zone_05_dur_Predator", "low_dur_Anxiety") 
save(anxiety_predator, file = "../Models/anxiety_predator.Rdata")

anxiety_aggression <- bivar_model("zone_05_dur_Aggression", "low_dur_Anxiety") 
save(anxiety_aggression, file = "../Models/anxiety_aggression.Rdata")

anxiety_social <- bivar_model("zone_05_dur_Social", "low_dur_Anxiety") 
save(anxiety_social, file = "../Models/anxiety_social.Rdata")

anxiety_novel <- bivar_model("zone_05_dur_Novel", "low_dur_Anxiety") 
save(anxiety_novel, file = "../Models/anxiety_novel.Rdata")

anxiety_activity <- bivar_model("tot_dist_Activity", "low_dur_Anxiety") 
save(anxiety_activity, file = "../Models/anxiety_activity.Rdata")




```

#Running bivar models for treatment and control groups separately
```{r}

anxiety_personality_wide_control <- subset(anxiety_personality_wide, anxiety_personality_wide$Group == "Control")
anxiety_personality_wide_treatment <- subset(anxiety_personality_wide, anxiety_personality_wide$Group == "Treatment")


bivar_model_control <- function(var1,var2, df = anxiety_personality_wide_control){
  df$response1 <- df[,var1]
  df$response2 <- df[,var2]
formula1 <- bf(response1 ~ Sex  + (1 | 2 |Fish_ID))
formula2 <- bf(response2 ~ Sex  + (1 | 2 |Fish_ID))
bivar_formula <- mvbrmsformula(formula1, formula2)
bivar <- brm(formula = bivar_formula,
                     data = df,
                     family = gaussian(),
                     chains = 4,
                     iter = 6000, warmup = 2000)
return(bivar)
}

bivar_model_treatment <- function(var1,var2, df = anxiety_personality_wide_treatment){
  df$response1 <- df[,var1]
  df$response2 <- df[,var2]
formula1 <- bf(response1 ~ Sex  + (1 | 2 |Fish_ID))
formula2 <- bf(response2 ~ Sex  + (1 | 2 |Fish_ID))
bivar_formula <- mvbrmsformula(formula1, formula2)
bivar <- brm(formula = bivar_formula,
                     data = df,
                     family = gaussian(),
                     chains = 4,
                     iter = 6000, warmup = 2000)
return(bivar)
}
```


#Control bivar models
```{r}
#Combinations required for bivar models
# low dur vs. zone_05_dur_aggression
# low dur vs. zone_05_dur_predator 
# low_dur vs. zone_05_dur_social
# low_dur vs. zone_05_dur_novel
# low_dur vs. tot_dist_activity

#NOTE: RESPONSE 1 IS ALWAYS THE FIRST TERM IN THE MODEL NAME EG. "PREDATOR_ANXIETY" RESPONSE 1 IS ANXIETY, RESPONSE 2 IS CONTROL

#run and save bivar models
predator_anxiety_control <- bivar_model_control("zone_05_dur_Predator", "low_dur_Anxiety") 
save(predator_anxiety_control, file = "../Models/predator_anxiety_control.Rdata")

aggression_anxiety_control <- bivar_model_control("zone_05_dur_Aggression", "low_dur_Anxiety") 
save(aggression_anxiety_control, file = "../Models/aggression_anxiety_control.Rdata")

social_anxiety_control <- bivar_model_control("zone_05_dur_Social", "low_dur_Anxiety") 
save(social_anxiety_control, file = "../Models/social_anxiety_control.Rdata")

novel_anxiety_control <- bivar_model_control("zone_05_dur_Novel", "low_dur_Anxiety") 
save(novel_anxiety_control, file = "../Models/novel_anxiety_control.Rdata")

activity_anxiety_control <- bivar_model_control("tot_dist_Activity", "low_dur_Anxiety") 
save(activity_anxiety_control, file = "../Models/activity_anxiety_control.Rdata")
```

Treatment bivar models
```{r}
predator_anxiety_treatment <- bivar_model_treatment("zone_05_dur_Predator", "low_dur_Anxiety") 
save(predator_anxiety_treatment, file = "../Models/predator_anxiety_treatment.Rdata")

aggression_anxiety_treatment <- bivar_model_treatment("zone_05_dur_Aggression", "low_dur_Anxiety") 
save(aggression_anxiety_treatment, file = "../Models/aggression_anxiety_treatment.Rdata")

social_anxiety_treatment <- bivar_model_treatment("zone_05_dur_Social", "low_dur_Anxiety") 
save(social_anxiety_treatment, file = "../Models/social_anxiety_treatment.Rdata")

novel_anxiety_treatment <- bivar_model_treatment("zone_05_dur_Novel", "low_dur_Anxiety") 
save(novel_anxiety_treatment, file = "../Models/novel_anxiety_treatment.Rdata")

activity_anxiety_treatment <- bivar_model_treatment("tot_dist_Activity", "low_dur_Anxiety") 
save(activity_anxiety_treatment, file = "../Models/activity_anxiety_treatment.Rdata")
```

#load bivar models
```{r}
load("../Models/predator_anxiety_control.Rdata")
load("../Models/aggression_anxiety_control.Rdata")
load("../Models/social_anxiety_control.Rdata")
load("../Models/novel_anxiety_control.Rdata")
load("../Models/activity_anxiety_control.Rdata")

load("../Models/predator_anxiety_treatment.Rdata")
load("../Models/aggression_anxiety_treatment.Rdata")
load("../Models/social_anxiety_treatment.Rdata")
load("../Models/novel_anxiety_treatment.Rdata")
load("../Models/activity_anxiety_treatment.Rdata")

```


#Population parameters control
```{r}
#Vector of model names to be able to use with lapply
bivar_models_anxiety_control <- c("predator_anxiety_control", "aggression_anxiety_control","social_anxiety_control", "novel_anxiety_control","activity_anxiety_control")

bivar_brm_func <- function(mod_char){
mod <- get(mod_char)
post <- as.data.frame(mod)

# use stringr::str_split for this
inter_key <- stringr::str_split(mod_char, "_")[[1]] 


behaviour1 <- inter_key[1]
behaviour2 <- inter_key[2]
response1 <- "response1"
response2 <- "response2"

# understand the parameters in the bivariate model:
names(post)
#what do we want to get?
#y = B0 + fish_ID + B1*treatment + B2*male+ B3*treatment*male 
cols <- names(post)
cols

B0_1 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, "Intercept") & ! stringr::str_detect(cols,"Fish")] 
B1_1 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, "GroupTreatment") & ! stringr::str_detect(cols,"Fish") & ! stringr::str_detect(cols, "Sex")] 
B2_1 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, "Sex") & ! stringr::str_detect(cols,"Fish") & ! stringr::str_detect(cols, "GroupTreatment")] 
B3_1 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, "Sex") & ! stringr::str_detect(cols,"Fish") & stringr::str_detect(cols, "GroupTreatment")]
B0_2 <- post[,stringr::str_detect(cols, response2)  & stringr::str_detect(cols, "Intercept") & ! stringr::str_detect(cols,"Fish")] 
B1_2 <- post[,stringr::str_detect(cols, response2)  & stringr::str_detect(cols, "GroupTreatment") & ! stringr::str_detect(cols,"Fish") & ! stringr::str_detect(cols, "Sex")] 
B2_2 <- post[,stringr::str_detect(cols, response2)  & stringr::str_detect(cols, "Sex") & ! stringr::str_detect(cols,"Fish") & ! stringr::str_detect(cols, "GroupTreatment")] 
B3_2 <- post[,stringr::str_detect(cols, response2)  & stringr::str_detect(cols, "Sex") & ! stringr::str_detect(cols,"Fish") & stringr::str_detect(cols, "GroupTreatment")]
sigma_ID1 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, "sd_Fish")]
sigma_ID2 <- post[,stringr::str_detect(cols, response2)  & stringr::str_detect(cols, "sd_Fish")]
cor_ID1_ID2 <- post[,stringr::str_detect(cols, response1)  & stringr::str_detect(cols, response2) & stringr::str_detect(cols, "cor_Fish")]
sigma_e1 <- post[,stringr::str_detect(cols, response1) & stringr::str_detect(cols, "sigma_")]
sigma_e2 <- post[,stringr::str_detect(cols, response2) & stringr::str_detect(cols, "sigma_")]
cor_e1_e2 <- post[,stringr::str_detect(cols, response1) & stringr::str_detect(cols, response2) & stringr::str_detect(cols, "rescor_")]
tot_var1 <- sigma_ID1 + sigma_e1
tot_var2 <- sigma_ID2 + sigma_e2
rpt1 <- sigma_ID1/tot_var1
rpt2 <- sigma_ID2/tot_var2


df <- data.frame(behaviour1,behaviour2, B0_1, B1_1, B2_1, B3_1, B0_2,B1_2,B2_2,B3_2,sigma_ID1,sigma_ID2,cor_ID1_ID2,sigma_e1,sigma_e2,cor_e1_e2,rpt1,rpt2)
return(df)
}

bivar_processed_control <- lapply(bivar_models_anxiety_control, function(x) bivar_brm_func(x))

bivar_combined_control <- dplyr::bind_rows(bivar_processed_control)


```

#Population parameters treatment
```{r}
#Vector of model names to be able to use with lapply
bivar_models_anxiety_treatment <- c("predator_anxiety_treatment", "aggression_anxiety_treatment","social_anxiety_treatment", "novel_anxiety_treatment","activity_anxiety_treatment")

bivar_processed_treatment <- lapply(bivar_models_anxiety_treatment, function(x) bivar_brm_func(x))

bivar_combined_treatment <- dplyr::bind_rows(bivar_processed_treatment)
```

#Contrast analysis between control and treatment
```{r}
#Rename columns

colnames(bivar_combined_control) <- c("behaviour1_control", "behaviour2_control","B0_1_control","B2_1_control","B0_2_control", "B2_2_control", "sigma_ID1_control", "sigma_ID2_control","cor_ID1_ID2_control","sigma_e1_control","sigma_e2_control","cor_e1_e2_control","rpt1_control","rpt2_control")

colnames(bivar_combined_treatment) <- c("behaviour1_treatment", "behaviour2_treatment","B0_1_treatment","B2_1_treatment","B0_2_treatment", "B2_2_treatment", "sigma_ID1_treatment", "sigma_ID2_treatment","cor_ID1_ID2_treatment","sigma_e1_treatment","sigma_e2_treatment","cor_e1_e2_treatment","rpt1_treatment","rpt2_treatment")

#Add columns together to create a new wide data frame

bivar_control_treatment <- dplyr::bind_cols(bivar_combined_control, bivar_combined_treatment)

#Checking model results same order
paste0(bivar_control_treatment$behaviour1_control, bivar_control_treatment$behaviour2_control) == paste0(bivar_control_treatment$behaviour1_treatment, bivar_control_treatment$behaviour2_treatment)

#All TRUE


#Getting treatment difference in variance components

names(bivar_control_treatment)

contrasts_var <- bivar_control_treatment %>% dplyr::mutate(sigma_ID1_treatment_minus_control=sigma_ID1_treatment-sigma_ID1_control,
                                   sigma_ID2_treatment_minus_control=sigma_ID2_treatment-sigma_ID2_control,
                                   cor_ID1_ID2_treatment_minus_control=cor_ID1_ID2_treatment-cor_ID1_ID2_control,
                                   sigma_e1_treatment_minus_control=sigma_e1_treatment-sigma_e1_control,
                                   sigma_e2_treatment_minus_control=sigma_e2_treatment-sigma_e2_control,
                                   cor_e1_e2_treatment_minus_control=cor_e1_e2_treatment-cor_e1_e2_control,
                                   rpt1_treatment_minus_control=rpt1_treatment-rpt1_control,
                                   rpt2_treatment_minus_control=rpt2_treatment-rpt2_control,
                                   mod_id=paste0(behaviour1_control, " vs ",behaviour2_control)) %>%
  dplyr::rename(behaviour1=behaviour1_control, behaviour2=behaviour2_control) %>%
  dplyr::select(behaviour1, behaviour2,mod_id,
         sigma_ID1_treatment_minus_control,
                                   sigma_ID2_treatment_minus_control,
                                   cor_ID1_ID2_treatment_minus_control,
                                   sigma_e1_treatment_minus_control,
                                   sigma_e2_treatment_minus_control,
                                   cor_e1_e2_treatment_minus_control,
                                   rpt1_treatment_minus_control,
                                   rpt2_treatment_minus_control,
         cor_ID1_ID2_treatment,
         cor_ID1_ID2_control)

#Contrasts 

contrasts_var %>% dplyr::group_by(mod_id) %>% dplyr::summarise(behav_syn_mean = mean(cor_ID1_ID2_treatment_minus_control), cor_control = mean(cor_ID1_ID2_control),cor_treatment = mean(cor_ID1_ID2_treatment))

#need to do separate data frames and then join 
df <- dplyr::bind_rows(lapply(split(contrasts_var, contrasts_var$mod_id), function(x)
  
data.frame(est=mean(x$cor_ID1_ID2_treatment_minus_control),
lower_bounds=quantile(x$cor_ID1_ID2_treatment_minus_control, 0.025),
upper_bounds=quantile(x$cor_ID1_ID2_treatment_minus_control, 0.975))))

df$mod_id <- unique(contrasts_var$mod_id)

df2 <- dplyr::bind_rows(lapply(split(contrasts_var, contrasts_var$mod_id), function(x)
  
data.frame(est=mean(x$cor_ID1_ID2_treatment),
lower_bounds=quantile(x$cor_ID1_ID2_treatment, 0.025),
upper_bounds=quantile(x$cor_ID1_ID2_treatment, 0.975))))

df2$mod_id <- unique(contrasts_var$mod_id)

rownames(df2) <- c("predator vs anxiety", "aggression vs anxiety", "social vs anxiety", "novel vs anxiety", "activity vs anxiety")

df2 <- df2 %>% mutate(mod_id = rownames(df2))

df3 <- dplyr::bind_rows(lapply(split(contrasts_var, contrasts_var$mod_id), function(x)
  
data.frame(est=mean(x$cor_ID1_ID2_control),
lower_bounds=quantile(x$cor_ID1_ID2_control, 0.025),
upper_bounds=quantile(x$cor_ID1_ID2_control, 0.975))))

df3$mod_id <- unique(contrasts_var$mod_id)

rownames(df3) <- c("predator vs anxiety", "aggression vs anxiety", "social vs anxiety", "novel vs anxiety", "activity vs anxiety")

df3 <- df3 %>% mutate(mod_id = rownames(df3))

df_joined <- bind_rows(df, df2, df3)

df_joined <- df_joined %>% mutate(condition = c("contrast", "contrast", "contrast", "contrast", "contrast", "treatment", "treatment","treatment", "treatment","treatment","control","control","control","control","control"))

#plot

#just for contrasts
ggplot(df) + 
geom_pointrange(aes(x = mod_id, y = est, ymin = lower_bounds, ymax = upper_bounds))+
geom_hline(yintercept=0, linetype="dotted")+
coord_flip()

#means and contrasts

anxiety_behav_plot <- ggplot(df_joined, aes(x=mod_id, y=est, colour=condition)) +
geom_errorbar(aes(ymin=lower_bounds, ymax=upper_bounds), width = 0.4, position = position_dodge(0.3), size=0.8) +
geom_point(aes(x = mod_id, y = est), position = position_dodge(0.3), size=3)+
geom_hline(yintercept = 0, lty = "dotted") +
coord_flip()+
   theme(axis.title.y=element_blank())+
  theme_classic()+
  scale_color_manual(values=c("#000000", "#DD8D29", "#E2D200"))+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +
  theme(axis.title.y=element_blank())+
   theme(legend.position = "bottom")+
    theme(legend.title=element_blank())+
  ggtitle("Behavioral Syndrome - (Anxiety & Personality)")
 
anxiety_behav_plot

```


















