---
title: "Scrap"
author: "Hamza"
date: "19/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import and subset data

First, we select a stimulus, which we want all the data for. Then with the function, we filter which videos have that stimulus in the first, second, third and fourth phase (via the time). Then we join all to create one dataset of that stimulus.
```{r}
Personality <- read.csv("./Data/Personality/ALL.csv")

# ROSE Q: have you tidied personality data to remove trials that were affected by covers falling down, etc.?
to_check <- Personality[Personality$Notes!="",] # check these ones

#HAMZA A: Apologies for the confusion. Those with the note "RE-RUN..." were fish that had to be re-run due to issues in a previous trial. Those fish are fine. Notes with a delay in time were also accounted for in Ethovision (by creating a unique setting for time). The other trials have been excluded. 

# ROSE request: fix mixing data for trial info
to_fix <- Personality[Personality$Date==""|Personality$Fish_ID=="",] # need date to know the age of the fish

# HAMZA A: Dates have been added. Sorry, again this was due to re-exporting from Ethovision and I forgot to add in certain details for the trial list. 


#Gathering all Social Data 

filter_etho(Personality, c("A","C","D","E","G","M"), ("6-9")) -> Social_Phase_1
filter_etho(Personality, c("J","K","L","P","U","X"), ("13-16")) -> Social_Phase_2
filter_etho(Personality, c("H","I","R","S","T","W"), ("20-23")) -> Social_Phase_3
filter_etho(Personality, c("B","F","N","O","Q","V"), ("27-30")) -> Social_Phase_4

Social_ALL <- bind_rows(Social_Phase_1,Social_Phase_2, Social_Phase_3, Social_Phase_4)



#Gathering all Predator Data

filter_etho(Personality, c("F","K","O","T","W","X"), ("6-9")) -> Predator_Phase_1
filter_etho(Personality, c("E","G","N","Q","R","S"), ("13-16")) -> Predator_Phase_2
filter_etho(Personality, c("B","C","M","P","U","V"), ("20-23")) -> Predator_Phase_3
filter_etho(Personality, c("A","D","H","I","J","L"), ("27-30")) -> Predator_Phase_4

Predator_ALL <- bind_rows(Predator_Phase_1,Predator_Phase_2, Predator_Phase_3, Predator_Phase_4)





#Gathering all Novel Data


filter_etho(Personality, c("B","H","J","N","P","R"), ("6-9")) -> Novel_Phase_1
filter_etho(Personality, c("A","I","M","O","V","W"), ("13-16")) -> Novel_Phase_2
filter_etho(Personality, c("D","F","G","L","Q","X"), ("20-23")) -> Novel_Phase_3
filter_etho(Personality, c("C","E","K","S","T","U"), ("27-30")) -> Novel_Phase_4

Novel_ALL <- bind_rows(Novel_Phase_1,Novel_Phase_2, Novel_Phase_3, Novel_Phase_4)





#Gathering all Aggression Data


filter_etho(Personality, c("I","L","Q","S","U","V"), ("6-9")) -> Aggression_Phase_1
filter_etho(Personality, c("B","C","D","F","H","T"), ("13-16")) -> Aggression_Phase_2
filter_etho(Personality, c("A","E","J","K","N","O"), ("20-23")) -> Aggression_Phase_3
filter_etho(Personality, c("G","M","P","R","W","X"), ("27-30")) -> Aggression_Phase_4

Aggression_ALL <- bind_rows(Aggression_Phase_1,Aggression_Phase_2, Aggression_Phase_3, Aggression_Phase_4)

#Subsetting data by control and treatment
Social_Control <- subset(Social_ALL, Social_ALL$Group == "Control") 
Social_Treatment <- subset(Social_ALL, Social_ALL$Group == "Treatment") 

Predator_Control <- subset(Predator_ALL, Predator_ALL$Group == "Control") 
Predator_Treatment <- subset(Predator_ALL, Predator_ALL$Group == "Treatment") 

Novel_Control <- subset(Novel_ALL, Novel_ALL$Group == "Control") 
Novel_Treatment <- subset(Novel_ALL, Novel_ALL$Group == "Treatment") 

Aggression_Control <- subset(Aggression_ALL, Aggression_ALL$Group == "Control") 
Aggression_Treatment <- subset(Aggression_ALL, Aggression_ALL$Group == "Treatment") 

# EXPLORATION DATA
# Acclimation <- read.csv("./Data/Personality/Acclimation.csv")
Post_assay <- read.csv("./Data/Personality/Post-assay.csv")
```

### ROSE: shorter code to Import and subset data   

```{r}
Personality <- read.csv("./Data/Personality/ALL.csv")

# making a column with a factor where the four levels correspond to the four phases
Personality$phase <-  factor(Personality$Time, levels = c("6-9", "13-16", "20-23", "27-30")) 

# making a list where each level of the list is a different phase
phases <- split(Personality, Personality$phase)

# function to apply to the four phases: 1, 2, 3, and 4
func_phase <- function(phase = 1){
    df <- phases[[phase]] # getting phase dataframe based on index (1-4)
    df$Behaviour <- df[,paste0("Phase",phase)] # getting columns that says which behaviour was in that phase
    df <- df[,!(names(df) %in% paste0("Phase", 1:4))] # removing the now-redunant Phase1,...,Phase4 columns
    return(df) # return dataframe
}

# applying function, returning a list of four dataframes
Personality_list <- lapply(1:4, function(x) func_phase(x))
Personality_df <- bind_rows(Personality_list) # stakes dataframe on top of each other

Aggression_ALL <- Personality_df[Personality_df$Behaviour == "Aggression",]
Novel_ALL <- Personality_df[Personality_df$Behaviour == "Novel",]
Predator_ALL <- Personality_df[Personality_df$Behaviour == "Predator",]
Social_ALL <- Personality_df[Personality_df$Behaviour == "Social",]

#Subsetting data by control and treatment
Social_Control <- subset(Social_ALL, Social_ALL$Group == "Control") 
Social_Treatment <- subset(Social_ALL, Social_ALL$Group == "Treatment") 

Predator_Control <- subset(Predator_ALL, Predator_ALL$Group == "Control") 
Predator_Treatment <- subset(Predator_ALL, Predator_ALL$Group == "Treatment") 

Novel_Control <- subset(Novel_ALL, Novel_ALL$Group == "Control") 
Novel_Treatment <- subset(Novel_ALL, Novel_ALL$Group == "Treatment") 

Aggression_Control <- subset(Aggression_ALL, Aggression_ALL$Group == "Control") 
Aggression_Treatment <- subset(Aggression_ALL, Aggression_ALL$Group == "Treatment") 

# EXPLORATION DATA
# Acclimation <- read.csv("../Data/Personality/Acclimation.csv")
Post_assay <- read.csv("./Data/Personality/Post-assay.csv")
```

### MAIN ANALYSIS 
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS FOR EACH GROUP AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITIES
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT

Exploration (Acclimation and post-stimulus); total distance traveled

```{r}


#Post assay

Model_post <- lmer(tot_dist_Activity ~ Group*Sex + (1 |Fish_ID), data = Post_assay) 
tab_model(Model_post)
hist(residuals(Model_post)) 

#Quick Visualization
Post_assay %>%
  ggplot(aes(Group, tot_dist_Activity, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)+
  facet_grid(~Sex)
```


Social Analysis - time spent near stimulus screen 
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Social_zone05 <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Social_ALL) 
tab_model(Model_Social_zone05)
hist(residuals(Model_Social_zone05)) 

Model_Social_zone052 <- lmer(zone_05_dur ~ Group*Sex + (1 | Fish_ID), data = Social_ALL) 
tab_model(Model_Social_zone052)
hist(residuals(Model_Social_zone052)) 

#Calculating repeatabilities using custom made functions
rpt_zone05(Social_Control) -> rpt_social_control
rpt_social_control
rpt_zone05(Social_Treatment) -> rpt_social_treatment
rpt_social_treatment

#Obtaining within-individual and between-individual variance 

rpt_within_zone05(Social_Control) -> within_between_social_control
within_between_social_control
rpt_within_zone05(Social_Treatment) -> within_between_social_treatment
within_between_social_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_social_boot <- unlist_rptr(rpt_social_control)
Treatment_social_boot <- unlist_rptr(rpt_social_treatment) 
social_diff <- difference_boot(Treatment_social_boot,Control_social_boot)  
q_social <- quantiles_diff_boot(social_diff) #obtaining 95% CI
m_social <- mean(social_diff) #Obtaining mean
m_social
q_social

# Calculating difference in variance between control and treatment groups
Model_Social1 <- lme(zone_05_dur ~ Group*Sex-1, random = ~ 1| Fish_ID, data = Social_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Social1)
Model_Social2 <- lme(zone_05_dur ~ Group*Sex-1, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Social_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Social2)
anova(Model_Social1, Model_Social2) #calculating difference between two models to find difference in variance

#Quick Visualization
Social_ALL %>%
  ggplot(aes(Group, zone_05_dur, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)+
  facet_grid(~Sex)
```

Social Analysis - mean speed
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Social_speed <- lmer(mean_speed ~ Group + Sex + (1 | Fish_ID), data = Social_ALL) 
tab_model(Model_Social_speed)
hist(residuals(Model_Social_speed)) 


#Calculating repeatabilities using custom made functions
rpt_speed(Social_Control) -> rpt_social_control_speed
rpt_social_control_speed
rpt_speed(Social_Treatment) -> rpt_social_treatment_speed
rpt_social_treatment_speed

#Obtaining within-individual and between-individual variance 

rpt_within_speed(Social_Control) -> within_between_social_control_speed
within_between_social_control_speed
rpt_within_speed(Social_Treatment) -> within_between_social_treatment_speed
within_between_social_treatment_speed

#Obtaining differences between repeatabilities using custom made functions
Control_social_boot_speed <- unlist_rptr(rpt_social_control_speed)
Treatment_social_boot_speed <- unlist_rptr(rpt_social_treatment_speed) 
social_diff_speed <- difference_boot(Treatment_social_boot_speed,Control_social_boot_speed)  
q_social_speed <- quantiles_diff_boot(social_diff_speed) #obtaining 95% CI
m_social_speed <- mean(social_diff_speed) #Obtaining mean
m_social_speed
q_social_speed

# Calculating difference in variance between control and treatment groups
Model_Social1_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Social_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Social1_speed)
Model_Social2_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Social_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Social2_speed)
anova(Model_Social1_speed, Model_Social2_speed) #calculating difference between two models to find difference in variance

#Quick Visualization
Social_ALL %>%
  ggplot(aes(Group, mean_speed, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Social Analysis - total distance

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Social_tot_dist <- lmer(tot_dist ~ Group + Sex + (1 | Fish_ID), data = Social_ALL) 
tab_model(Model_Social_tot_dist)
hist(residuals(Model_Social_tot_dist)) 

Model_Social_tot_dist2 <- lmer(tot_dist ~ Group*Sex + (1 | Fish_ID), data = Social_ALL) 
tab_model(Model_Social_tot_dist2)
hist(residuals(Model_Social_tot_dist2)) 

#Calculating repeatabilities using custom made functions
rpt_tot_dist(Social_Control) -> rpt_social_control_dist
rpt_social_control_dist
rpt_tot_dist(Social_Treatment) -> rpt_social_treatment_dist
rpt_social_treatment_dist

#Obtaining within-individual and between-individual variance 

rpt_within_tot_dist(Social_Control) -> within_between_social_control_dist
within_between_social_control_dist
rpt_within_tot_dist(Social_Treatment) -> within_between_social_treatment_dist
within_between_social_treatment_dist

#Obtaining differences between repeatabilities using custom made functions
Control_social_boot_dist <- unlist_rptr(rpt_social_control_dist)
Treatment_social_boot_dist <- unlist_rptr(rpt_social_treatment_dist) 
social_diff_dist <- difference_boot(Treatment_social_boot,Control_social_boot)  
q_social_dist <- quantiles_diff_boot(social_diff_dist) #obtaining 95% CI
m_social_dist <- mean(social_diff_dist) #Obtaining mean
m_social_dist
q_social_dist

# Calculating difference in variance between control and treatment groups
Model_Social1_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, data = Social_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Social1_dist)
Model_Social2_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Social_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Social2_dist)
anova(Model_Social1_dist, Model_Social2_dist) #calculating difference between two models to find difference in variance

#Quick Visualization
Social_ALL %>%
  ggplot(aes(Group, tot_dist, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```


Predator Analysis - time spent near stimulus screen 
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Predator_zone05 <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Predator_ALL) 
tab_model(Model_Predator_zone05)
hist(residuals(Model_Predator_zone05)) 


#Calculating repeatabilities using custom made functions
rpt_zone05(Predator_Control) -> rpt_predator_control
rpt_predator_control
rpt_zone05(Predator_Treatment) -> rpt_predator_treatment
rpt_predator_treatment

#Obtaining within-individual and between-individual variance 

rpt_within_zone05(Predator_Control) -> within_between_predator_control
within_between_predator_control
rpt_within_zone05(Predator_Treatment) -> within_between_predator_treatment
within_between_predator_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_predator_boot <- unlist_rptr(rpt_predator_control)
Treatment_predator_boot <- unlist_rptr(rpt_predator_treatment) 
predator_diff <- difference_boot(Treatment_predator_boot,Control_predator_boot)  
q_predator <- quantiles_diff_boot(predator_diff) #obtaining 95% CI
m_predator <- mean(positive_diff) #Obtaining mean
m_predator
q_predator

# Calculating difference in variance between control and treatment groups
Model_Predator1 <- lme(zone_05_dur ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Predator_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Predator1)
Model_Predator2 <- lme(zone_05_dur ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Predator_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Predator2)
anova(Model_Predator1, Model_Predator2) #calculating difference between two models to find difference in variance

#Quick Visualization
Predator_ALL %>%
  ggplot(aes(Group, zone_05_dur, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Predator Analysis - mean speed
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Predator_speed <- lmer(mean_speed ~ Group + Sex + (1 | Fish_ID), data = Predator_ALL) 
tab_model(Model_Predator_speed)
hist(residuals(Model_Predator_speed)) 


#Calculating repeatabilities using custom made functions
rpt_speed(Predator_Control) -> rpt_predator_control_speed
rpt_predator_control_speed
rpt_speed(Predator_Treatment) -> rpt_predator_treatment_speed
rpt_predator_treatment_speed

#Obtaining within-individual and between-individual variance 

rpt_within_speed(Predator_Control) -> within_between_predator_control_speed
within_between_predator_control_speed
rpt_within_speed(Predator_Treatment) -> within_between_predator_treatment_speed
within_between_predator_treatment_speed

#Obtaining differences between repeatabilities using custom made functions
Control_predator_boot_speed <- unlist_rptr(rpt_predator_control_speed)
Treatment_predator_boot_speed <- unlist_rptr(rpt_predator_treatment_speed) 
predator_diff_speed <- difference_boot(Treatment_predator_boot_speed,Control_predator_boot_speed)  
q_predator_speed <- quantiles_diff_boot(predator_diff_speed) #obtaining 95% CI
m_predator_speed <- mean(predator_diff_speed) #Obtaining mean
m_predator_speed
q_predator_speed

# Calculating difference in variance between control and treatment groups
Model_Predator1_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Predator_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Predator1_speed)
Model_Predator2_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Predator_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Predator2_speed)
anova(Model_Predator1_speed, Model_Predator2_speed) #calculating difference between two models to find difference in variance

#Quick Visualization
Predator_ALL %>%
  ggplot(aes(Group, mean_speed, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Predator Analysis - total distance

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Predator_tot_dist <- lmer(tot_dist ~ Group + Sex + (1 | Fish_ID), data = Predator_ALL) 
tab_model(Model_Predator_tot_dist)
hist(residuals(Model_Predator_tot_dist)) 

Model_Predator_tot_dist2 <- lmer(tot_dist ~ Group*Sex + (1 | Fish_ID), data = Predator_ALL) 
tab_model(Model_Predator_tot_dist2)
hist(residuals(Model_Predator_tot_dist2)) 

#Calculating repeatabilities using custom made functions
rpt_tot_dist(Predator_Control) -> rpt_predator_control_dist
rpt_predator_control_dist
rpt_tot_dist(Predator_Treatment) -> rpt_predator_treatment_dist
rpt_predator_treatment_dist

#Obtaining within-individual and between-individual variance 

rpt_within_tot_dist(Predator_Control) -> within_between_predator_control_dist
within_between_predator_control_dist
rpt_within_tot_dist(Predator_Treatment) -> within_between_predator_treatment_dist
within_between_predator_treatment_dist

#Obtaining differences between repeatabilities using custom made functions
Control_predator_boot_dist <- unlist_rptr(rpt_predator_control_dist)
Treatment_predator_boot_dist <- unlist_rptr(rpt_predator_treatment_dist) 
predator_diff_dist <- difference_boot(Treatment_predator_boot,Control_predator_boot)  
q_predator_dist <- quantiles_diff_boot(predator_diff_dist) #obtaining 95% CI
m_predator_dist <- mean(predator_diff_dist) #Obtaining mean
m_predator_dist
q_predator_dist

# Calculating difference in variance between control and treatment groups
Model_Predator1_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, data = Predator_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Predator1_dist)
Model_Predator2_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Predator_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Predator2_dist)
anova(Model_Predator1_dist, Model_Predator2_dist) #calculating difference between two models to find difference in variance

#Quick Visualization
Predator_ALL %>%
  ggplot(aes(Group, tot_dist, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```


Novel Analysis - time spent near stimulus screen 
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Novel_zone05 <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Novel_ALL) 
tab_model(Model_Novel_zone05)
hist(residuals(Model_Novel_zone05)) #data skewed, needs transformation

Model_Novel_zone052 <- lmer(sqrt(zone_05_dur) ~ Group + Sex + (1 | Fish_ID), data = Novel_ALL) 
tab_model(Model_Novel_zone052)
hist(residuals(Model_Novel_zone052))


#Calculating repeatabilities using custom made functions
rpt_zone05(Novel_Control) -> rpt_novel_control
rpt_novel_control
rpt_zone05(Novel_Treatment) -> rpt_novel_treatment
rpt_novel_treatment

#Obtaining within-individual and between-individual variance 

rpt_within_zone05(Novel_Control) -> within_between_novel_control
within_between_novel_control
rpt_within_zone05(Novel_Treatment) -> within_between_novel_treatment
within_between_novel_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_novel_boot <- unlist_rptr(rpt_novel_control)
Treatment_novel_boot <- unlist_rptr(rpt_novel_treatment) 
novel_diff <- difference_boot(Control_novel_boot,Treatment_novel_boot)  
q_novel <- quantiles_diff_boot(novel_diff) #obtaining 95% CI
m_novel <- mean(novel_diff) #Obtaining mean
m_novel
q_novel

# Calculating difference in variance between control and treatment groups
Model_Novel1 <- lme(sqrt(zone_05_dur) ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Novel_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Novel1)
Model_Novel2 <- lme(sqrt(zone_05_dur) ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Novel_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Novel2)
anova(Model_Novel1, Model_Novel2) #calculating difference between two models to find difference in variance

#Quick Visualization
Novel_ALL %>%
  ggplot(aes(Group, zone_05_dur, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Novel Analysis - mean speed
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Novel_speed <- lmer(mean_speed ~ Group + Sex + (1 | Fish_ID), data = Novel_ALL) 
tab_model(Model_Novel_speed)
hist(residuals(Model_Novel_speed)) 


#Calculating repeatabilities using custom made functions
rpt_speed(Novel_Control) -> rpt_novel_control_speed
rpt_novel_control_speed
rpt_speed(Novel_Treatment) -> rpt_novel_treatment_speed
rpt_novel_treatment_speed

#Obtaining within-individual and between-individual variance 

rpt_within_speed(Novel_Control) -> within_between_novel_control_speed
within_between_novel_control_speed
rpt_within_speed(Novel_Treatment) -> within_between_novel_treatment_speed
within_between_novel_treatment_speed

#Obtaining differences between repeatabilities using custom made functions
Control_novel_boot_speed <- unlist_rptr(rpt_novel_control_speed)
Treatment_novel_boot_speed <- unlist_rptr(rpt_novel_treatment_speed) 
novel_diff_speed <- difference_boot(Control_novel_boot_speed,Treatment_novel_boot_speed)  
q_novel_speed <- quantiles_diff_boot(novel_diff_speed) #obtaining 95% CI
m_novel_speed <- mean(novel_diff_speed) #Obtaining mean
m_novel_speed
q_novel_speed

# Calculating difference in variance between control and treatment groups
Model_Novel1_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Novel_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Novel1_speed)
Model_Novel2_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Novel_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Novel2_speed)
anova(Model_Novel1_speed, Model_Novel2_speed) #calculating difference between two models to find difference in variance

#Quick Visualization
Novel_ALL %>%
  ggplot(aes(Group, mean_speed, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Novel Analysis - total distance

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Novel_tot_dist <- lmer(tot_dist ~ Group + Sex + (1 | Fish_ID), data = Novel_ALL) 
tab_model(Model_Novel_tot_dist)
hist(residuals(Model_Novel_tot_dist)) 

Model_Novel_tot_dist2 <- lmer(tot_dist ~ Group*Sex + (1 | Fish_ID), data = Novel_ALL) 
tab_model(Model_Novel_tot_dist2)
hist(residuals(Model_Novel_tot_dist2)) 

#Calculating repeatabilities using custom made functions
rpt_tot_dist(Novel_Control) -> rpt_novel_control_dist
rpt_novel_control_dist
rpt_tot_dist(Novel_Treatment) -> rpt_novel_treatment_dist
rpt_novel_treatment_dist

#Obtaining within-individual and between-individual variance 

rpt_within_tot_dist(Novel_Control) -> within_between_novel_control_dist
within_between_novel_control_dist
rpt_within_tot_dist(Novel_Treatment) -> within_between_novel_treatment_dist
within_between_novel_treatment_dist

#Obtaining differences between repeatabilities using custom made functions
Control_novel_boot_dist <- unlist_rptr(rpt_novel_control_dist)
Treatment_novel_boot_dist <- unlist_rptr(rpt_novel_treatment_dist) 
novel_diff_dist <- difference_boot(Treatment_novel_boot,Control_novel_boot)  
q_novel_dist <- quantiles_diff_boot(novel_diff_dist) #obtaining 95% CI
m_novel_dist <- mean(novel_diff_dist) #Obtaining mean
m_novel_dist
q_novel_dist

# Calculating difference in variance between control and treatment groups
Model_Novel1_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, data = Novel_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Novel1_dist)
Model_Novel2_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Novel_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Novel2_dist)
anova(Model_Novel1_dist, Model_Novel2_dist) #calculating difference between two models to find difference in variance

#Quick Visualization
Novel_ALL %>%
  ggplot(aes(Group, tot_dist, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Aggression Analysis - time spent near stimulus screen 
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Aggression_zone05 <- lmer(zone_05_dur ~ Group + Sex + (1 | Fish_ID), data = Aggression_ALL) 
tab_model(Model_Aggression_zone05)
hist(residuals(Model_Aggression_zone05)) 


#Calculating repeatabilities using custom made functions
rpt_zone05(Aggression_Control) -> rpt_aggression_control
rpt_aggression_control
rpt_zone05(Aggression_Treatment) -> rpt_aggression_treatment
rpt_aggression_treatment

#Obtaining within-individual and between-individual variance 

rpt_within_zone05(Aggression_Control) -> within_between_aggression_control
within_between_aggression_control
rpt_within_zone05(Aggression_Treatment) -> within_between_aggression_treatment
within_between_aggression_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_aggression_boot <- unlist_rptr(rpt_aggression_control)
Treatment_aggression_boot <- unlist_rptr(rpt_aggression_treatment) 
aggression_diff <- difference_boot(Treatment_aggression_boot,Control_aggression_boot)  
q_aggression <- quantiles_diff_boot(aggression_diff) #obtaining 95% CI
m_aggression <- mean(aggression_diff) #Obtaining mean
m_aggression
q_aggression

# Calculating difference in variance between control and treatment groups
Model_Aggression1 <- lme(zone_05_dur ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Aggression_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Aggression1)
Model_Aggression2 <- lme(zone_05_dur ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Aggression_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Aggression2)
anova(Model_Aggression1, Model_Aggression2) #calculating difference between two models to find difference in variance

#Quick Visualization
Aggression_ALL %>%
  ggplot(aes(Group, zone_05_dur, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Aggression Analysis - mean speed
```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Aggression_speed <- lmer(mean_speed ~ Group + Sex + (1 | Fish_ID), data = Aggression_ALL) 
tab_model(Model_Aggression_speed)
hist(residuals(Model_Aggression_speed)) 


#Calculating repeatabilities using custom made functions
rpt_speed(Aggression_Control) -> rpt_aggression_control_speed
rpt_aggression_control_speed
rpt_speed(Aggression_Treatment) -> rpt_aggression_treatment_speed
rpt_aggression_treatment_speed

#Obtaining within-individual and between-individual variance 

rpt_within_speed(Aggression_Control) -> within_between_aggression_control_speed
within_between_aggression_control_speed
rpt_within_speed(Aggression_Treatment) -> within_between_aggression_treatment_speed
within_between_aggression_treatment_speed

#Obtaining differences between repeatabilities using custom made functions
Control_aggression_boot_speed <- unlist_rptr(rpt_aggression_control_speed)
Treatment_aggression_boot_speed <- unlist_rptr(rpt_aggression_treatment_speed) 
aggression_diff_speed <- difference_boot(Control_aggression_boot_speed,Treatment_aggression_boot_speed)  
q_aggression_speed <- quantiles_diff_boot(aggression_diff_speed) #obtaining 95% CI
m_aggression_speed <- mean(aggression_diff_speed) #Obtaining mean
m_aggression_speed
q_aggression_speed

# Calculating difference in variance between control and treatment groups
Model_Aggression1_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, data = Aggression_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Aggression1_speed)
Model_Aggression2_speed <- lme(mean_speed ~ Group-1 + Sex, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Aggression_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Aggression2_speed)
anova(Model_Aggression1_speed, Model_Aggression2_speed) #calculating difference between two models to find difference in variance

#Quick Visualization
Aggression_ALL %>%
  ggplot(aes(Group, mean_speed, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

Aggression Analysis - total distance

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Aggression_tot_dist <- lmer(tot_dist ~ Group + Sex + (1 | Fish_ID), data = Aggression_ALL) 
tab_model(Model_Aggression_tot_dist)
hist(residuals(Model_Aggression_tot_dist)) 

Model_Aggression_tot_dist2 <- lmer(tot_dist ~ Group*Sex + (1 | Fish_ID), data = Aggression_ALL) 
tab_model(Model_Aggression_tot_dist2)
hist(residuals(Model_Aggression_tot_dist2)) 

#Calculating repeatabilities using custom made functions
rpt_tot_dist(Aggression_Control) -> rpt_aggression_control_dist
rpt_aggression_control_dist
rpt_tot_dist(Aggression_Treatment) -> rpt_aggression_treatment_dist
rpt_aggression_treatment_dist

#Obtaining within-individual and between-individual variance 

rpt_within_tot_dist(Aggression_Control) -> within_between_aggression_control_dist
within_between_aggression_control_dist
rpt_within_tot_dist(Aggression_Treatment) -> within_between_aggression_treatment_dist
within_between_aggression_treatment_dist

#Obtaining differences between repeatabilities using custom made functions
Control_aggression_boot_dist <- unlist_rptr(rpt_aggression_control_dist)
Treatment_aggression_boot_dist <- unlist_rptr(rpt_aggression_treatment_dist) 
aggression_diff_dist <- difference_boot(Treatment_aggression_boot,Control_aggression_boot)  
q_aggression_dist <- quantiles_diff_boot(aggression_diff_dist) #obtaining 95% CI
m_aggression_dist <- mean(aggression_diff_dist) #Obtaining mean
m_aggression_dist
q_aggression_dist

# Calculating difference in variance between control and treatment groups
Model_Aggression1_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, data = Aggression_ALL, na.action=na.exclude) #mixed model without variance structure
summary(Model_Aggression1_dist)
Model_Aggression2_dist <- lme(tot_dist ~ Group*Sex-1, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Group), data = Aggression_ALL, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Aggression2_dist)
anova(Model_Aggression1_dist, Model_Aggression2_dist) #calculating difference between two models to find difference in variance

#Quick Visualization
Aggression_ALL %>%
  ggplot(aes(Group, tot_dist, fill=Group)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

## ROSE: looking at residuals
```{r}
# load("~/Dropbox/Shinichi/Postdoc/F0_Chapter_Analysis/Scripts/myEnvironment.RData")
hist(residuals(Model_acclimation))                                    
hist(residuals(Model_post))                                           
hist(residuals(Model_Social_zone05))  # negatively skewed                                 
hist(residuals(Model_Social_zone052)) # negatively skewed                                   
hist(residuals(Model_Social_speed))   # positively skewed                                
hist(residuals(Model_Social_tot_dist))# positively skewed                                 
hist(residuals(Model_Social_tot_dist2))# positively skewed                               
hist(residuals(Model_Predator_zone05))# positively skewed                                
hist(residuals(Model_Predator_speed))                                 
hist(residuals(Model_Predator_tot_dist))                              
hist(residuals(Model_Predator_tot_dist2))                             
hist(residuals(Model_Novel_zone05)) # positively skewed
hist(residuals(Model_Novel_zone052)) # tails too fat                                  
hist(residuals(Model_Novel_speed)) # tails too skinny                                   
hist(residuals(Model_Novel_tot_dist)) # negatively skewed                                 
hist(residuals(Model_Novel_tot_dist2)) # negatively skewed                                
hist(residuals(Model_Aggression_zone05))                              
hist(residuals(Model_Aggression_speed)) # tails too thin                             
hist(residuals(Model_Aggression_tot_dist)) # tails too thin                             
hist(residuals(Model_Aggression_tot_dist2))  # tails too thin  
```

###Example correlation analysis 

Attempting to do some practic and wrap my head around the process
```{r}
brm_correlation_Social_Activity <- brm(cbind(scale(zone_05_dur_Social), scale(tot_dist_Activity)) ~ Group*Sex + (1 | Fish_ID),
                                  data = Personality_wide,
                                  family = gaussian(),
                                  chains = 3,
                                  iter = 2000, warmup = 1000)



save(brm_correlation_Social_Activity, file = "../Models/brm_correlation_Social_Activity.Rdata")

summary(brm_correlation_Social_Activity)

colnames(posterior_samples(brm_correlation_Social_Activity))[1:18]

Correlation_Time_Spent_Social_Dist_Travel <- posterior_samples(brm_correlation_Social_Activity)[,13] # ROSE2: always call things by their names, not their index. Reduces mistakes, makes code easier to read + more reproducible.
par(mar=c(2, 2, 3, 2))
plot(density(Correlation_Time_Spent_Social_Dist_Travel),
main="Correlation Time Spent - Total Distance Travelled",
xlab="",ylab="",cex.main=0.8)
abline(v=0,col="red",lwd=2)
abline(v=mean(Correlation_Time_Spent_Social_Dist_Travel),col="black",lwd=2)
abline(v=HPDinterval(as.mcmc(Correlation_Time_Spent_Social_Dist_Travel))[1],col="black",lty=2)
abline(v=HPDinterval(as.mcmc(Correlation_Time_Spent_Social_Dist_Travel))[2],col="black",lty=2)

#Can asume a significant positive correlation between time spent near stimulus screen during social stimulus and total distance travelled in actvity phase. Dashed lines indicate the 95% credible interval of the posterior distribution.Does not cross zero.

# For demonstrative purposes we can anyways go ahead and plot the among individual correlation of behaviors. For this we need to extract the posterior mean behavioral types (BLUP) and calculate the slope between behaviors.

#Extract BLUPS


  

#Calculating slope

#COV(X,Y ) = (CORX,Y * sqrt(VarX) * sqrt(VarY )


cov.social_dist <-
posterior_samples(Correlation_Time_Spent_Social_Dist_Travel)[,13] *
sqrt(posterior_samples(Correlation_Time_Spent_Social_Dist_Travel)[,9]^2) *
sqrt(posterior_samples(Correlation_Time_Spent_Social_Dist_Travel)[,10]^2)

var.dist <- posterior_samples(m4_brm)[,10]^2

Social_Distance_slope <- cov.social_dist / var.dist
```
